\documentclass{amsart}

% \usepackage{fontspec}
% \setmainfont{Libertinus Serif}
% \setsansfont{Libertinus Sans}
% \setmonofont{Liberation Mono}

\usepackage[style=alphabetic, backref, giveninits, maxbibnames=10]{biblatex}
\addbibresource{o-minimal.bib}

\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsmath, amsfonts, amssymb, mathtools, amsthm}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xurl}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric,arrows,cd}

\tikzstyle{notions} = [rectangle, rounded corners,
minimum width=3cm,
minimum height=1cm,
text centered,
draw=black,
fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

\usepackage{tcolorbox}

\newtheorem{theorem}{Theorem}[subsection]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{construction}[theorem]{Construction}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\numberwithin{equation}{section}

\newcommand{\definable}{\mathrm{def}}
\newcommand{\analytic}{\mathrm{an}}


\title{Notes on o-minimality}
\author{Tang Zhichao}
\date{\today}

\begin{document}

\maketitle

\section{Basic model theory}
Materials follow from \cite{zbMATH01821671,zbMATH01160037},
mainly \cite{zbMATH01821671}.
\subsection{Languages and Structures}
The goal of this section is to describe what is o-minimality
from a model theoretic aspect,
therefore some logical preliminaries are required.
Some standard theory related to the real numbers
will be proved to be o-minimal,
not only about polynomials, but can include the exponential function and analytic functions.

\subsubsection{Basic definitions}
In mathematical logic,
we use first-order languages to describe mathematical structures.
Intuitively, a structure is a set that we wish to study equipped with a collection of distinguished functions, relations, and elements.
We then choose a language where we can talk about the distinguished functions, relations, and elements and nothing more.

\begin{definition}
  A \emph{language $\mathcal{L}$} is given by specifying the following data:
  \begin{enumerate}[label = {(\roman*)}]
    \item a set of function symbols $\mathcal{F}$ and positive integers $n_f$ for each $f \in \mathcal{F}$;
    \item a set of relation symbols $\mathcal{R}$ and positive integers $n_R$ for each $R \in \mathcal{R}$;
    \item a set of constant symbols $\mathcal{C}$.
  \end{enumerate}
\end{definition}

\begin{definition}
  An \emph{$\mathcal{L}$-structure $\mathcal{M}$} is given by the following data:
  \begin{enumerate}[label = {(\roman*)}]
    \item a nonempty set $M$ called the universe, domain, or underlying set of $\mathcal{M}$;
    \item a function $f^{\mathcal{M}} : M^{n_f} \to M$ for each $f \in \mathcal{F}$;
    \item a set $R^{\mathcal{M}} \subseteq M^{n_R}$ for each $R \in \mathcal{R}$;
    \item an element $c^{\mathcal{M}} \in M$ for each $c \in \mathcal{C}$.
  \end{enumerate}
\end{definition}

\begin{definition}
  Suppose that $\mathcal{M}$ and $\mathcal{N}$ are $\mathcal{L}$-structures with universes $M$ and $N$, respectively.
  An \emph{$\mathcal{L}$-embedding} is a one-to-one (injective) map $\eta: M \to N$
  that preserves the interpretation of all of the symbols of $\mathcal{L}$.
  \begin{enumerate}[label = {(\roman*)}]
    \item $\eta(f^{\mathcal{M}}(a_1,\dots,a_{n_f})) = f^{\mathcal{N}}(\eta(a_1),\dots,\eta(a_{n_f}))$
      for all $f\in \mathcal{F}$ and $a_1,\dots,a_{n_f} \in M$;
    \item $(a_1,\dots,a_{n_R}) \in R^{\mathcal{M}}$ if and only if
      $(\eta(a_1),\dots,\eta(a_{n_R})) \in R^{\mathcal{N}}$ for all $R \in \mathcal{R}$ and $a_1,\dots,a_{n_R} \in M$;
    \item $\eta(c^{\mathcal{M}}) = c^{\mathcal{N}}$ for all $c \in \mathcal{C}$.
  \end{enumerate}
  A bijective $\mathcal{L}$-embedding is called an \emph{$\mathcal{L}$-isomorphism}.
  If $M \subseteq N$ and the inclusion map is an $\mathcal{L}$-embedding,
  $\mathcal{M}$ is a \emph{substructure} of $\mathcal{N}$ or that
  $\mathcal{N}$ is an \emph{extension} of $\mathcal{M}$.
\end{definition}

The \emph{cardinality} of $\mathcal{M}$ is $|M|$,
the cardinality of the universe of $\mathcal{M}$.
If $\eta: \mathcal{M} \to \mathcal{N}$ is an embedding then
the cardinality of $\mathcal{N}$ is at least the cardinality of $\mathcal{M}$.

\begin{definition}
  The set of \emph{$\mathcal{L}$-terms} is the smallest set $\mathcal{T}$ such that
  \begin{enumerate}[label = {(\roman*)}]
    \item $c\in \mathcal{T}$ for each constant symbol $c \in \mathcal{C}$,
    \item each variable symbol $v_i \in \mathcal{T}$ for $i = 1,2,\dots$, and
    \item if $t_1,\dots,t_{n_f} \in \mathcal{T}$ and $f \in \mathcal{F}$, then $f(t_1,\dots,t_{n_f}) \in \mathcal{T}$.
  \end{enumerate}
\end{definition}

\begin{definition}
  $\phi$ is an \emph{atomic $\mathcal{L}$-formula} if $\phi$ is either
  \begin{enumerate}[label= {\roman*)}]
    \item $t_1 = t_2$, where $t_1$ and $t_2$ are terms, or
    \item $R(t_1,\dots,t_{n_R})$, where $R \in \mathcal{R}$ and $t_1,\dots,t_{n_R}$ are terms.
  \end{enumerate}
  The set of \emph{$\mathcal{L}$-formulas} is the smallest set $\mathcal{W}$ containing the atomic formulas such that
  \begin{enumerate}[label= {\roman*)}]
    \item if $\phi$ is in $\mathcal{W}$, then $\neg\phi$ is in $\mathcal{W}$,
    \item if $\phi$ and $\psi$ are in $\mathcal{W}$, then $(\phi \land \psi)$ and $(\phi \lor \psi)$ are in $\mathcal{W}$, and
    \item if $\phi$ is in $\mathcal{W}$, then $\exists v_i\, \phi$ and $\forall v_i\, \phi$ are in $\mathcal{W}$.
  \end{enumerate}
\end{definition}

A variable $v$ \emph{occurs freely} in a formula $\phi$
if it is not inside a $\exists v$ or $\forall v$ quantifier;
otherwise, it is \emph{bound}.
A formula is a \emph{sentence} if it has no free variables.

\begin{definition}
  Let $\phi$ be a formula with free variables from
  $\overline{v} = (v_{i_1},\dots,v_{i_m})$, and let
  $\overline{a} = (a_{i_1},\dots,a_{i_m})\in M^m$.
  Inductively define \emph{$\mathcal{M} \models \phi(\overline{a})$} as follows.
  \begin{enumerate}[label = {\roman*)}]
    \item If $\phi$ is $t_1 = t_2$, then $\mathcal{M} \models \phi(\overline{a})$
      if $t_1^{\mathcal{M}}(\overline{a}) = t_2^{\mathcal{M}}(\overline{a})$.
    \item If $\phi$ is $R(t_1,\dots,t_{n_R})$, then $\mathcal{M} \models \phi(\overline{a})$
      if $(t^{\mathcal{M}}_1(\overline{a}),\dots,t^{\mathcal{M}}_{n_R}(\overline{a})) \in R^{\mathcal{M}}$.
    \item If $\phi$ is $\neg \psi$, then $\mathcal{M} \models \phi(\overline{a})$ if $\mathcal{M} \not\models \psi(\overline{a})$.
    \item If $\phi$ is $(\psi \land \theta)$, then $\mathcal{M} \models \phi(\overline{a})$
      if $\mathcal{M} \models \psi(\overline{a})$ and $\mathcal{M} \models \theta(\overline{a})$.
    \item If $\phi$ is $(\psi \lor \theta)$, then $\mathcal{M} \models \phi(\overline{a})$
      if $\mathcal{M} \models \psi(\overline{a})$ or $\mathcal{M} \models \theta(\overline{a})$.
    \item If $\phi$ is $\exists v_j \psi(\overline{v},v_j)$, then $\mathcal{M} \models \phi(\overline{a})$
      if there is $b \in M$ such that $\mathcal{M} \models \psi(\overline{a},b)$.
    \item If $\phi$ is $\forall v_j \psi(\overline{v},v_j)$,
      then $\mathcal{M} \models \phi(\overline{a})$ if $\mathcal{M} \models \psi(\overline{a},b)$ for all $b \in M$.
  \end{enumerate}
  If $\mathcal{M} \models \phi(\overline{a})$ we say that
  $\mathcal{M}$ \emph{satisfies} $\phi(\overline{a})$ or $\phi(\overline{a})$ is \emph{true} in $\mathcal{M}$.
\end{definition}

\begin{proposition}
  Suppose that $\mathcal{M}$ is a substructure of $\mathcal{N}$,
  $\overline{a} \in M$, and $\phi(\overline{v})$ is a quantifier-free formula.
  Then, $\mathcal{M} \models \phi(\overline{a})$ if and only if $\mathcal{N} \models \phi(\overline{a})$.
\end{proposition}

\begin{definition}
  Two $\mathcal{L}$-structures $\mathcal{M}$ and $\mathcal{N}$ are \emph{elementarily equivalent}
  and denote $\mathcal{M} \equiv \mathcal{N}$ if
  \[
    \mathcal{M} \models \phi \text{ if and only if }\mathcal{N} \models \phi
  \]
  for all $\mathcal{L}$-sentences $\phi$.
\end{definition}

\subsubsection{Theories and logical consequence}
Let $\mathrm{Th}(\mathcal{M})$, the \emph{full theory} of $\mathcal{M}$,
be the set of $\mathcal{M}$-sentences $\phi$ such that $\mathcal{M} \models \phi$.

$\mathcal{M} \equiv \mathcal{N}$ if and only if $\mathrm{Th}(\mathcal{M}) = \mathrm{Th}(\mathcal{N})$.

\begin{theorem}
  Suppose that $j: \mathcal{M} \to \mathcal{N}$ is an isomorphism.
  Then, $\mathcal{M} \equiv \mathcal{N}$.
\end{theorem}

Let $\mathcal{L}$ be a language.
An \emph{$\mathcal{L}$-theory $T$} is a set of $\mathcal{L}$-sentences.

$\mathcal{M}$ is a \emph{model} of $T$ and denote $\mathcal{M} \models T$ if $\mathcal{M} \models \phi$ for all sentences $\phi \in T$.

A theory is \emph{satisfiable} if it has a model.

A class of $\mathcal{L}$-structures $\mathcal{K}$ is an \emph{elementary class}
if there is an $\mathcal{L}$-theory $T$ such that $\mathcal{K} = \{ \mathcal{M}:\mathcal{M} \models T \}$.
The sentences in $T$ are called \emph{axioms} for the elementary class.

\begin{definition}
  Let $T$ be an $\mathcal{L}$-theory and $\phi$ an $\mathcal{L}$-sentence.
  $\phi$ is a \emph{logical consequence} of $T$ and denote $T \models \phi$ if $\mathcal{M} \models \phi$
  whenever $\mathcal{M} \models T$.
\end{definition}

\subsubsection{Definability and Interpretability}
\begin{definition}
  Let $\mathcal{M} = (M,\dots)$ be an $\mathcal{L}$-structure.
  $X \subseteq M^n$ is \emph{definable} if and only if there is an $\mathcal{L}$-formula $\phi(v_1,\dots,v_n,w_1,\dots,w_m)$
  and $\overline{b} \in M^m$ such that $X = \{ \overline{a} \in M^n : \mathcal{M} \models \phi(\overline{a},\overline{b}) \}$.
  $\phi(\overline{v},\overline{b})$ \emph{defines} $X$.

  $X$ is \emph{$A$-definable }or \emph{definable over $A$} if there is a formula $\psi(\overline{v},w_1,\dots,w_l)$ and
  $\overline{b} \in A^l$ such that $\psi(\overline{v},\overline{b})$ defines $X$.
\end{definition}

\begin{lemma}
  Let $\mathcal{L}_r$ be the language of ordered rings and
  $(\mathbb{R}, +, -, \cdot, <, 0, 1)$ be the ordered field of real numbers.
  Suppose that $X \subset \mathbb{R}^n$ is $A$-definable.
  Then, the topological closure of $X$ is also $A$-definable.
\end{lemma}

\begin{proposition}[Concrete Characterization of Definable Sets]
  Let $\mathcal{M}$ be an $\mathcal{L}$-structure.
  Suppose that $D_n$ is a collection of subsets of $M^n$ for all $n \ge 1$ and
  $\mathcal{D} = (D_n : n \ge 1)$ is the smallest collection such that:
  \begin{enumerate}[label = {\roman*)}]
    \item $M^n \in D_n$;
    \item for all $n$-ary function symbols $f$ of $\mathcal{L}$, the graph of $f^{\mathcal{M}}$ is in $D_{n+1}$;
    \item for all $n$-ary relation symbols $R$ of $\mathcal{L}$, $R^{\mathcal{M}} \in D_n$;
    \item for all $i$, $j\le n$, $\{(x_1,\dots,x_n)\in M^n : x_i = x_j\} \in D_n$;
    \item if $X \in D_n$, then $M \times X \in D_{n+1}$;
    \item each $D_n$ is closed under complement, union, and intersection;
    \item if $X \in D_{n+1}$ and $\pi: M^{n+1} \to M^n$ is the projection map $(x_1,\dots,x_{n+1}) \mapsto (x_1,\dots,x_n)$,
      then $\pi(X) \in D_n$;
    \item if $X \in D_{n+m}$ and $b \in M^m$, then $\{a\in M^n: (a,b) \in X \} \in D_n$.
  \end{enumerate}
  Then, $X \subseteq M^n$ is definable if and only if $X \in D_n$.
\end{proposition}

\begin{proposition}
  Let $\mathcal{M}$ be an $\mathcal{L}$-structure.
  If $X \subset M^n$ is $A$-definable,
  then every $\mathcal{L}$-automorphism of $\mathcal{M}$ that fixes $A$ pointwise fixes $X$ setwise.
\end{proposition}

\begin{definition}
  An $\mathcal{L}_0$-structure $\mathcal{N}$ is \emph{definably interpreted} in an $\mathcal{L}$-structure $\mathcal{M}$
  if and only if one can find a definable $X \subseteq M^n$ for some $n$ and can interpret the symbols of $\mathcal{L}_0$
  as definable subsets and functions on $X$ (definable using $\mathcal{L}$)
  so that the resulting $\mathcal{L}_0$-structure is isomorphic to $\mathcal{N}$.

  An $\mathcal{L}_0$-structure $\mathcal{N}$ is \emph{interpretable} in an $\mathcal{L}$-structure $\mathcal{M}$
  if there is a definable $X \subseteq M^n$, a definable equivalence relation $E$ on $X$,
  and for each symbol of $\mathcal{L}_0$, one can find definable $E$-invariant sets on $X$
  such that $X / E$ with the induced structure is isomorphic to $\mathcal{N}$.
\end{definition}

Let $S$ be a set.
The universe of a \emph{many-sorted structure} $\mathcal{N}$ with sorts $S$ is
a set $N$ that is partitioned into disjoint sets $\{N_i : i \in S\}$.
For each $n$-ary relation symbol $R$,
there are $s_1,\dots,s_n \in S$ such that $R^{\mathcal{N}} \subset N^{s_1} \times \dots \times N^{s_n}$.
For each $n$-ary function symbol $f$,
there are $s_0,\dots,s_n \in S$ such that $f^{\mathcal{N}} : N^{s_1} \times \dots \times N^{s_n} \to N^{s_0}$.

Let $\mathcal{M}$ be an $\mathcal{L}$-structure.
The set of sorts $S = \{S_E : E$ an $\emptyset$-definable equivalence relation on $M^n$ for some $n$ $\}$.
In the many-sorted structure $\mathcal{M}^{\mathrm{eq}}$,
one interpret the sort $S_E$ as $M^n / E$ for $E$ an $\emptyset$-definable equivalence relation on $M^n$.
Because $=$ is a definable equivalence relation on $M$,
$M$ can be identified with the sort $S_{=}$.
All relations and functions of $\mathcal{L}$ are relations and functions on $M^k$.
For each $\emptyset$-definable equivalence relation $E$ on $M^n$,
we have in $\mathcal{M}^{\mathrm{eq}}$ an $n$-ary function $f_E: M^n \to S_E$ given by $f_E(\overline{x}) = \overline{x} / E$.

\begin{lemma}
  \begin{enumerate}[label = {\roman*)}]
    \item If $X \subseteq M^n$ is definable in $\mathcal{M}^{\mathrm{eq}}$, then $X$ is definable in $\mathcal{M}$.
    \item If $\mathcal{M} \equiv \mathcal{N}$, then $\mathcal{M}^{\mathrm{eq}} \equiv \mathcal{N}^{\mathrm{eq}}$.
    \item If $\sigma$ is an automorphism of $\mathcal{M}^{\mathrm{eq}}$, then $\sigma|M$ is an automorphism of $\mathcal{M}$.
    \item If $\sigma$ is an automorphism of $\mathcal{M}$,
      there is $\widehat{\sigma}$ an automorphism of $\mathcal{M}^{\mathrm{eq}}$ such that $\sigma = \widehat{\sigma}|M$.
  \end{enumerate}
\end{lemma}

\subsection{Basic Techniques and Important Results}
\subsubsection{Completeness and Compactness}
Let $T$ be an $\mathcal{L}$-theory and $\phi$ an $\mathcal{L}$-sentence.
A proof of $\phi$ from $T$ is a finite sequence of $\mathcal{L}$-formulas
$\psi_1,\dots,\psi_m$ such that $\psi_m = \phi$ and $\psi_i \in T$ or
$\psi_i$ follows from $\psi_1,\dots,\psi_{i-1}$ by a simple logical rule for each $i$.

Denote $T \vdash \phi$ if there is a proof of $\phi$ from $T$.

Some properties of the proof system:
\begin{enumerate}[label = {$\bullet$}]
  \item Proofs are finite.
  \item (Soundness) If $T \vdash \phi$, then $T \models \phi$.
  \item If $T$ is a finite set of sentences, then there is an algorithm that,
    when given a sequence of $\mathcal{L}$-formulas $\sigma$ and an $\mathcal{L}$-sentence $\phi$,
    will decide whether $\sigma$ is a proof of $\phi$ from $T$.
\end{enumerate}

A language $\mathcal{L}$ is \emph{recursive} if there is an algorithm that
decides whether a sequence of symbols is an $\mathcal{L}$-formula.
An $\mathcal{L}$-theory $T$ is recursive if there is a algorithm that,
when given an $\mathcal{L}$-sentence $\phi$ as input, decides whether $\phi \in T$.

\begin{theorem}[G\"odel's Completeness Theorem]
  Let $T$ be an $\mathcal{L}$-theory and $\phi$ an $\mathcal{L}$-sentence, then $T \models \phi$ if and only if $T\vdash \phi$.
\end{theorem}

\begin{definition}
  An $\mathcal{L}$-theory $T$ is \emph{inconsistent}
  if $T \vdash (\phi \land\neg\phi)$ for some sentence $\phi$;
  otherwise $T$ is \emph{consistent}.
\end{definition}

\begin{theorem}[Compactness Theorem]
  $T$ is satisfiable if and only if every finite subset of $T$ is satisfiable.
\end{theorem}

\begin{definition}
  A theory $T$ is \emph{finitely satisfiable} if every finite subset of $T$ is satisfiable.
\end{definition}

% \begin{definition}
%     An $\mathcal{L}$-theory $T$ has the \emph{witness property} if
%     whenever $\phi(v)$ is an $\mathcal{L}$-formula with one free variable $v$,
%     then there is a constant symbol $c \in \mathcal{L}$ such that
%     $T \models (\exists v\, \phi(v) \to \phi(c))$.
% \end{definition}

\begin{definition}
  An $\mathcal{L}$-theory $T$ is \emph{maximal} if for all $\phi$ either $\phi \in T$ or $\neg \phi \in T$.
\end{definition}

% \begin{lemma}
%     Suppose that $T$ is a maximal and finitely satisfiable $\mathcal{L}$-theory with witness property.
%     Then, $T$ has a model.
%     In fact, if $\kappa$ is a cardinal and $\mathcal{L}$ has at most $\kappa$ constant symbols, then there exists $\mathcal{M} \models T$ with $|\mathcal{M}| \le \kappa$.
% \end{lemma}

% \begin{lemma}
%     Let $T$ be a finitely satisfiable $\mathcal{L}$-theory.
%     There is a language $\mathcal{L}^* \supseteq \mathcal{L}$ and $T^* \supseteq T$ a finitely satisfiable $\mathcal{L}^*$-theory such that any $\mathcal{L}^*$-theory extending $T^*$ has the witness property.
%     $\mathcal{L}^*$ can be chosen such that $|\mathcal{L}^*| = |\mathcal{L}| + \aleph_0$.
% \end{lemma}

\begin{lemma}
  Suppose that $T$ is a finitely satisfiable $\mathcal{L}$-theory and $\phi$ is an $\mathcal{L}$-sentence, then,
  either $T \cup \{\phi\}$ or $T \cup \{\neg\phi\}$ is satisfiable.
\end{lemma}

\begin{corollary}
  If $T$ is a finitely satisfiable $\mathcal{L}$-theory,
  then there is a maximal finitely satisfiable $\mathcal{L}$-theory $T' \supseteq T$.
\end{corollary}

% \begin{theorem}
%   If $T$ is a finitely satisfiable $\mathcal{L}$-theory and $\kappa$ is an infinite cardinal with $\kappa \ge |\mathcal{L}|$,
%   then there is a model of $T$ of cardinality at most $\kappa$.
% \end{theorem}

% \begin{lemma}
%   If $T \models \phi$, then $\Delta \models \phi$ for some finite $\Delta \subseteq T$.
% \end{lemma}

\begin{definition}
  An $\mathcal{L}$-theory $T$ is called \emph{complete} if for any $\mathcal{L}$-sentence $\phi$,
  either $T \models \phi$ or $T \models \neg\phi$.
\end{definition}

% \begin{proposition}
%   Let $T$ be an $\mathcal{L}$-theory with infinite models.
%   If $\kappa$ is an infinite cardinal and $\kappa \ge |\mathcal{L}|$,
%   then there is a model of $T$ of cardinality $\kappa$.
% \end{proposition}

\begin{definition}
  Let $\kappa$ be an infinite cardinal and let $T$ be a theory with models of size $\kappa$.
  $T$ is \emph{$\kappa$-categorical} if any two models of $T$ of cardinal $\kappa$ are isomorphic.
\end{definition}

\begin{tcolorbox}
  Some abbreviation for commonly used theories:
  \begin{enumerate}[label = {}]
    \item \textbf{DLO}: dense linear order;
    \item \textbf{ACF}: algebraic closed field;
    \item \textbf{RCF}: real closed field;
    \item \textbf{DCF}: differential closed field.
  \end{enumerate}
\end{tcolorbox}

Let $\mathbf{ACF_p}$ be the theory of algebraically closed fields of characteristic $p$,
where $p$ is either $0$ or a prime number.

\begin{proposition}
  $\mathbf{ACF}_p$ is $\kappa$-categorical for all uncountable cardinals $\kappa$.
\end{proposition}

\begin{theorem}[Vaught's Test]
  Let $T$ be a satisfiable theory with no finite models that is
  $\kappa$-categorical for some infinite cardinal $\kappa \ge |\mathcal{L}|$.
  Then $T$ is complete.
\end{theorem}

% \begin{definition}
%     An $\mathcal{L}$-theory $T$ is \emph{decidable} if there is an algorithm that
%     when given an $\mathcal{L}$-sentence $\phi$ as input decides whether $T \models \phi$.
% \end{definition}

% \begin{lemma}
%     Let $T$ be a recursive complete satisfiable theory in a recursive language $\mathcal{L}$.
%     Then $T$ is decidable.
% \end{lemma}

% \begin{corollary}
%     For $p = 0$ or $p$ prime, $\mathbf{ACF}_p$ is decidable.
% \end{corollary}

\begin{corollary}
  Let $\phi$ be a sentence in the language of rings.
  The following are equivalent.
  \begin{enumerate}[label = {\roman*)}]
    \item $\phi$ is true in the complex numbers.
    \item $\phi$ is true in every algebraically closed field of characteristic zero.
    \item $\phi$ is true in some algebraically closed field of characteristic zero.
    \item There are arbitrarily large primes $p$ such that $\phi$ is true in some algebraically closed field of characteristic $p$.
    \item There is an $m$ such that for all $p > m$, $\phi$ is true in all algebraically closed fields of characteristic $p$.
  \end{enumerate}
\end{corollary}

\subsubsection{Between structures}
\begin{definition}
  If $\mathcal{M}$ and $\mathcal{N}$ are $\mathcal{L}$-structures,
  then an $\mathcal{L}$-embedding $j: \mathcal{M} \to \mathcal{N}$ is called an \emph{elementary embedding} if
  \[
    \mathcal{M} \models \phi(a_1,\dots,a_n) \iff \mathcal{N} \models \phi(j(a_1),\dots,j(a_n))
  \]
  for all $\mathcal{L}$-formulas $\phi(v_1,\dots,v_n)$ and all $a_1,\dots,a_n \in M$.

  If $\mathcal{M}$ is a substructure of $\mathcal{N}$,
  it is called an \emph{elementary substructure} and
  denote $\mathcal{M} \prec \mathcal{N}$ if the inclusion map is elementary,
  equivalently, $\mathcal{N}$ is an \emph{elementary extension} of $\mathcal{M}$.
\end{definition}

\begin{definition}
  Suppose that $\mathcal{M}$ is an $\mathcal{L}$-structure.
  Let $\mathcal{L}_M$ be the language where we add to $\mathcal{L}$ constant symbols $m$ for each element of $M$.
  The \emph{atomic diagram} of $\mathcal{M}$ is
  $\{\phi(m_1,\dots,m_n):\phi$ is either an atomic $\mathcal{L}$-formula or the negation of an atomic $\mathcal{L}$-formula and $\mathcal{M} \models \phi(m_1,\dots,m_n)\}$.
  The \emph{elementary diagram} of $\mathcal{M}$ is
  \[
    \phi(m_1,\dots,m_n): \mathcal{M} \models \phi(m_1,\dots,m_n),\text{$\phi$ is an $\mathcal{L}$-formula}.
  \]
  Let $\mathrm{Diag}(\mathcal{M})$ and $\mathrm{Diag_el}(\mathcal{M})$ denote the atomic and elementary diagrams of $\mathcal{M}$, respectively.
\end{definition}

\begin{theorem}[Upward L\"owenheim--Skolem Theorem]
  Let $\mathcal{M}$ be an infinite $\mathcal{L}$-structure and
  $\kappa$ be an infinite cardinal $\kappa \ge |\mathcal{M}| + |\mathcal{L}|$.
  Then, there is $\mathcal{N}$ an $\mathcal{L}$-structure of cardinality $\kappa$ and $j: \mathcal{M} \to \mathcal{N}$ is elementary.
\end{theorem}

\begin{proposition}[Tarski--Vaught Test]
  Suppose that $\mathcal{M}$ is a substructure of $\mathcal{N}$.
  Then, $\mathcal{M}$ is an elementary substructure if and only if,
  for any formula $\phi(v,\overline{w})$ and $\overline{a} \in M$,
  if there is $b \in N$ such that $\mathcal{N} \models \phi(b,\overline{a})$,
  there is $c \in M$ such that $\mathcal{N} \models \phi(c,\overline{a})$.
\end{proposition}

% An $\mathcal{L}$-theory $T$ has \emph{built-in Skolem functions}
% if for all $\mathcal{L}$-formulas $\phi(v,w_1,\dots,w_n)$ there is a function symbol $f$
% such that $T \models \forall \overline{w} ((\exists v \phi(v,\overline{w})) \to \phi(f(\overline{w}),\overline{w}))$.
% In other words, there are enough function symbols in the language to witness all existential statements.

% \begin{lemma}
%   Let $T$ be an $\mathcal{L}$-theory.
%   There are $\mathcal{L}^* \supseteq \mathcal{L}$and $T^* \supseteq T$ an $\mathcal{L}^*$-theory
%   such that $T^*$ has built-in Skolem functions,
%   and if $\mathcal{M} \models T$,
%   then $\mathcal{M}$ can be expanded to $\mathcal{M}^* \models T^*$.
%   $\mathcal{L}^*$ can be chosen such that $|\mathcal{L}^*|= |\mathcal{L}|+\aleph_0$.

%   We call $T^*$ a skolemization of $T$.
% \end{lemma}

\begin{theorem}[L\"owenheim--Skolem Theorem]
  Suppose $\mathcal{M}$ is an $\mathcal{L}$-structure and
  $X \subseteq M$, there is an elementary submodel $\mathcal{N}$ of $\mathcal{M}$
  such that $X \subseteq N$ and $|\mathcal{N}| \le |X| + |\mathcal{L}| + \aleph_0$.
\end{theorem}

\begin{definition}
  A \emph{universal sentence} is one of the form
  $\forall \overline{v} \phi(\overline{v})$,
  where $\phi$ is quantifier-free.
  An $\mathcal{L}$-theory $T$ has a \emph{universal axiomatization} if there is a set of universal $\mathcal{L}$-sentences $\Gamma$
  such that $\mathcal{M} \models \Gamma$ if and only if $\mathcal{M} \models T$ for all $\mathcal{L}$-structures $\mathcal{M}$.
\end{definition}

\begin{theorem}
  An $\mathcal{L}$-theory $T$ has a universal axiomatization if and only if
  whenever $\mathcal{M} \models T$ and $\mathcal{N}$ is a substructure of $\mathcal{M}$,
  then $\mathcal{N} \models T$.
\end{theorem}

\begin{definition}
  Suppose that $(I,<)$ is a linear order.
  Suppose that $\mathcal{M}_i$ is an $\mathcal{L}$-structure for $i \in I$.
  $(\mathcal{M}_i: i \in I)$ is a \emph{chain} of $\mathcal{L}$-structures if $\mathcal{M}_i \subseteq \mathcal{M}_j$ for $i < j$.
  If $\mathcal{M}_i \prec \mathcal{M}_j$ for $i < j$,
  $(\mathcal{M}_i: i \in I)$ is an \emph{elementary chain}.
\end{definition}

\begin{proposition}
  Suppose that $(I,<)$ is a linear order and
  $(\mathcal{M}_i: i \in I)$ is an elementary chain.
  Then, $\mathcal{M} = \bigcup_{i\in I} M_i$ is an elementary extension of each $\mathcal{M}_i$.
\end{proposition}

\begin{definition}
  A theory $T$ has a \emph{$\forall\exists$-axiomatization} if it can be axiomatized by sentences of
  the form $\forall v_1\dots\forall v_n \exists w_1\dots \exists w_m \phi(\overline{v},\overline{w})$
  where $\phi$ is a quantifier-free formula.
\end{definition}

\begin{definition}
  $\mathcal{M} \models T$ is \emph{existentially closed}
  if whenever $\mathcal{N} \models T$, $\mathcal{N} \supseteq \mathcal{M}$,
  and $\mathcal{N} \models \exists \overline{v}\, \phi(\overline{v},\overline{a})$,
  where $\overline{a} \in M$ and $\phi$ is quantifier-free,
  then $\mathcal{M} \models \exists \overline{v} \, \phi(\overline{v},\overline{a})$.
\end{definition}

\begin{definition}[Ultrafilters]
  Let $I$ be a set and $\mathcal{P}(I) = \{ X : X \subset I\}$
  denote the power set of $I$.
  A \emph{filter} on $I$ is a collection $D \subset \mathcal{P}(I)$ such that:
  \begin{enumerate}[label = {\roman*)}]
    \item $I \in D$, $\emptyset \not\in D$;
    \item if $A$, $B \in D$, then $A \cap B \in D$;
    \item if $A\in D$ and $A \subseteq B \subseteq I$, then $B \in D$.
  \end{enumerate}
  Examples:
  \begin{enumerate}
    \item Let $\kappa$ be an infinite cardinal with $\kappa \le |I|$.
      $D = \{ X \subseteq I : |I \backslash X| < \kappa\}$ is a filter.
      If $\kappa = \aleph_0$, $D$ is called the \emph{Fr\'echet filter}.
    \item For $x \in I$, $D = \{X\subseteq I: x\in X\}$ is a filter on $I$, called the \emph{principal filter}.
  \end{enumerate}

  A filter $D$ on $I$ is an \emph{ultrafilter} if $X \in D$ or $I\backslash X \in D$ for all $X \subseteq I$.
\end{definition}

\begin{definition}[Ultraproducts]
  Let $\mathcal{L}$ be a language and suppose that $I$ is an infinite set.
  Suppose that $\mathcal{M}_i$ is an $\mathcal{L}$-structure for each $i \in I$.
  Let $D$ be an ultrafilter on $I$.
  Define a new structure $\mathcal{M} = \prod \mathcal{M}_i / D$,
  which is called the \emph{ultraproduct} of the $\mathcal{M}_i$ using $D$.
  Define a relation $\sim$ on
  \[
    X = \prod_{i\in I}M_i = \Bigl\{ f: I \to \bigcup_{i\in I}M_i : f(i)\in M_i \text{ for all $i$} \Bigr\}
  \]
  by $f\sim g$ if and only if $\{i \in I:f(i) = g(i)\} \in D$.

  The universe of $\mathcal{M}$ will be $M = X / \sim$.

  If $c$ is a constant symbol of $\mathcal{L}$,
  let $c^{\mathcal{M}}$ be the $\sim$ class of $f_c \in X$ where $f_c(i) = c^{\mathcal{M}_i}$ for all $i\in I$.

  If $f$ is an $n$-ary function symbol of $\mathcal{L}$.
  Suppose that $g_1,\dots,g_n,h_1,\dots,h_n\in X$,
  and $g_i \sim h_i$ for $i = 1, \dots,n$.
  Define $g_{n+1}(i) = f^{\mathcal{M}_i}(g_1(i),\dots,g_n(i))$ and
  $h_{n+1}(i) = f^{\mathcal{M}_i}(h_1(i),\dots,h_n(i))$ for $i \in I$.
  Then one can show $g_{n+1} \sim h_{n+1}$.
  Thus $f^{\mathcal{M}}(g_1/\sim,\dots,g_n/\sim) = g_{n+1}/\sim$ determines a well-defined function on $\mathcal{M}$.

  Suppose that $R$ is a relation symbol of $\mathcal{L}$ and
  $g_1,\dots,g_n,h_1,\dots,h_n\in X$ as above.
  Then $\{i\in I: (g_1(i),\dots,g_n(i)) \in R^{\mathcal{M}_i}\} \in D$ if and only if
  $\{i \in I: (h_1(i),\dots,h_n(i)) \in R^{\mathcal{M}_i}\} \in D$.
  One can interpret
  \[
    R^{\mathcal{M}} = \{(g_1/\sim,\dots,g_m/\sim): \{ i\in I: (g_1(i),\dots,g_m(i)) \in R^{\mathcal{M}_i}\} \in D\}.
  \]
\end{definition}

\begin{definition}
  Let $\mathcal{M}$ be a fixed $\mathcal{L}$-structure,
  and $\mathcal{M}_i = \mathcal{M}$ for every $i \in \omega$.
  Let $D$ be a non-principal ultrafilter on $\omega$.
  Let $\mathcal{M}^* = \prod \mathcal{M}_i / D$,
  which is called an \emph{ultrapower} of $\mathcal{M}$.
\end{definition}

\begin{theorem}[Keisler--Shelah Theorem]
  Two $\mathcal{L}$-structures $\mathcal{M}$ and $\mathcal{N}$ are elementarily equivalent
  if and only if there is an index set $I$ and an ultrafilter $D$ on $I$ such that $\prod \mathcal{M}/D \cong \prod \mathcal{N}/D$.
\end{theorem}

\subsection{Algebraic Examples and Quantifiers}

\begin{center}
\begin{tcolorbox}[title = Properties of theories]
\begin{center}
\begin{tikzpicture}
\node[notions] (q-e) at (-2,0) {quantifier elimination};
\node[notions] (m-c) at (-2,-2) {model-complete};
\node[notions] (a-p-m) at (2,-2) {algebraically prime model};
\node (cc) at (0,-3.5) {+};
\node[notions] (c) at (0,-5) {complete};

\draw[arrow] (q-e) -- (m-c);
\draw[thick] (m-c) -- (cc);
\draw[thick] (a-p-m) -- (cc);
\draw[arrow] (cc) -- (c);
\end{tikzpicture}
\end{center}
\end{tcolorbox}
\end{center}

The study of definable sets is often made quite complicated by quantifiers.

\begin{definition}
  A theory $T$ has \emph{quantifier elimination} if for every formula $\phi$ there is a quantifier-free formula $\psi$ such that
  \[
    T \models \phi \leftrightarrow \psi.
  \]
\end{definition}

\begin{definition}
  An $\mathcal{L}$-theory $T$ is \emph{strongly minimal} if for any $\mathcal{M} \models T$
  every definable subset of $M$ is either finite or cofinite.
\end{definition}

\begin{definition}
  If $T$ is a theory then $T_{\forall}$ is the set of all universal consequences of $T$.
  $\mathcal{A} \models T_{\forall}$ if and only if there is $\mathcal{M} \models T$ with $\mathcal{A} \subseteq \mathcal{M}$.

  A theory $T$ has \emph{algebraically prime models}
  if for any $\mathcal{A} \models T_{\forall}$ there is
  $\mathcal{M} \models T$ and an embedding $i:\mathcal{A} \to \mathcal{M}$
  such that for all $\mathcal{N} \models T$ and embedding $j: \mathcal{A} \to \mathcal{N}$
  there is $h: \mathcal{M} \to \mathcal{N}$ such that $j = h \circ i$.

  If $\mathcal{M}$, $\mathcal{N} \models T$ and $\mathcal{M} \subseteq \mathcal{N}$,
  $\mathcal{M}$ is \emph{simply closed} in $\mathcal{N}$ and denote
  $\mathcal{M} \prec_s \mathcal{N}$ if for any quantifier free formula
  $\phi(\overline{v},w)$ and any $\overline{a} \in M$,
  if $\mathcal{N} \models \exists w\, \phi(\overline{a},w)$,
  then so does $\mathcal{M}$.
\end{definition}

\begin{definition}
  An $\mathcal{L}$-theory $T$ is \emph{model-complete} if,
  $\mathcal{M} \prec \mathcal{N}$ whenever
  $\mathcal{M} \subseteq \mathcal{N}$  and $\mathcal{M}$, $\mathcal{N} \models T$.
\end{definition}

\begin{proposition}
  If $T$ has quantifier eliminations,
  then $T$ is model-complete.
\end{proposition}

\begin{proposition}
  Let $T$ be a model-complete theory.
  Suppose that there is $\mathcal{M}_0 \models T$ such that $\mathcal{M}_0$ embeds into every model of $T$.
  Then, $T$ is complete.
\end{proposition}

\begin{definition}
  An ordered structure $(M,<,\dots)$ is \emph{o-minimal} if
  for any definable $X \subset M$,
  there are finitely many intervals $I_1,\dots,I_m$ with endpoints in $M \cup \{\pm\infty\}$
  and a finite set $X_0$ such that $X = X_0 \cup I_1 \cup \dots \cup I_m$.
\end{definition}

\subsubsection{Algebraic Closed Fields}

% \begin{lemma}
%     $\mathbf{ACF}_{\forall}$ is the theory of integral domains.
% \end{lemma}

\begin{theorem}
  $\mathbf{ACF}$ has quantifier elimination.
\end{theorem}

\begin{corollary}
  $\mathbf{ACF}$ is model-complete and $\mathbf{ACF}_p$ is complete where $p = 0$ or $p$ is prime.
\end{corollary}

% Let $K$ be a field.
% $X \subseteq K^n$ is \emph{Zariski closed} if $X = V(S)$ for some $S \subseteq K[X_1,\dots,X_n]$.

% \begin{lemma}
%   Let $K$ be a field.
%   The subsets of $K^n$ defined by atomic formulas are exactly those of the form $V(p)$ for some $p \in K[\overline{X}]$.
%   A subset of $K^n$ is quantifier-free definable if and only if it is a Boolean combination of Zariski closed sets.
% \end{lemma}

\begin{corollary}
  Let $K$ be an algebraically closed field.
  \begin{enumerate}[label = {\roman*)}]
    \item $X \subset K^n$ is constructable if and only if it is definable.
    \item (Chevalley's Theorem) The image of a constructable set under a polynomial map is constructable.
  \end{enumerate}
\end{corollary}

\begin{corollary}
  $\mathbf{ACF}$ is a strongly minimal theory.
\end{corollary}

\subsubsection{Real Closed Fields}

\begin{definition}
  A field $F$ is \emph{orderable} if there is a linear order $<$ of $F$ making $(F,<)$ an ordered field.

  F is \emph{formally real} if $-1$ is not a sum of squares.
\end{definition}

\begin{theorem}
  If $F$ is a formally real field, then $F$ is orderable.
\end{theorem}

\begin{definition}
  A field $F$ is \emph{real closed} if it is formally real with no proper formally real algebraic extensions.
\end{definition}

\begin{theorem}
  Let $F$ be a formally real field. The following are equivalent.
  \begin{enumerate}[label = {\roman*)}]
    \item $F$ is real closed.
    \item $F(i)$ is algebraically closed.
    \item For any $a\in F$, either $a$ or $-a$ is a square and every polynomial of odd degree has a root.
  \end{enumerate}
\end{theorem}

\begin{corollary}
  The class of real closed field is an elementary class of
  $\mathcal{L}_r$-structures.
\end{corollary}

\begin{definition}
  Let $\mathbf{RCF}$ be the $\mathcal{L}_{or}$-theory axiomatized by the axioms for real closed fields
  and the axioms for ordered fields.

  If $F$ is a formally real field, a \emph{real closure} of $F$ is a real closed algebraic extension of $F$.
\end{definition}

% \begin{theorem}
%   If $(F,<)$ is an ordered field,
%   and $R_1$ and $R_2$ are real closures of $F$ where the canonical ordering extends the ordering of $F$,
%   then there is a unique field isomorphism $\phi: R_1 \to R_2$ that is identity on $F$.
% \end{theorem}

\begin{corollary}
  $\mathbf{RCF}$ has algebraically prime models.
\end{corollary}

\begin{theorem}
  The theory $\mathbf{RCF}$ admits elimination of quantifiers in $\mathcal{L}_{or}$.
\end{theorem}

\begin{corollary}
  $\mathbf{RCF}$ is complete, model complete, and decidable.
\end{corollary}

\subsection{Semialgebraic Sets and O-minimality}
\begin{definition}
  Let $F$ be an ordered field.
  $X \subset F^n$ is \emph{semialgebraic} if it is a Boolean combination of sets of the form $\{\overline{x}:p(\overline{x})>0\}$,
  where $p(\overline{X}) \in F[X_1,\dots,X_n]$.

  A function is semialgebraic if its graph is semialgebraic.
\end{definition}

\begin{corollary}[Tarski--Seidenberg Theorem]
  The semialgebraic sets are closed under projection.
\end{corollary}

\begin{corollary}
  If $F \models \mathbf{RCF}$ and $A \subseteq F^n$ is semialgebraic,
  then the closure (topological) of $F$ is semialgebraic.
\end{corollary}

\begin{definition}
  Let $F$ be a real closed field and
  $f(\overline{X}) \in F(X_1,\dots,X_n)$ be a rational function.
  $f$ is \emph{positive semi-definite} if $f(\overline{a}) \ge 0$ for all $\overline{a} \in F^n$.
\end{definition}

\begin{theorem}[Hilbert's 17th Problem]
  If $f$ is a positive semi-definite rational function over a real closed field $F$,
  then $f$ is a sum of squares of rational functions.
\end{theorem}

\begin{corollary}
  $\mathbf{RCF}$ is an o-minimal theory.
\end{corollary}

\begin{lemma}
  If $f:\mathbb{R} \to \mathbb{R}$ is semialgebraic,
  then for any open interval $U \subseteq \mathbb{R}$,
  there is a point $x\in U$ such that $f$ is continuous at $x$.
\end{lemma}

\begin{corollary}
  Let $F$ be a real closed field and $f: F \to F$ is a semialgebraic function.
  Then, one can partition $F$ into $I_1\cup \dots \cup I_m\cup X$,
  where $X$ is finite and the $I_j$ are pairwise disjoint open intervals with endpoints in $F\cup \{\pm\infty\}$
  such that $f$ is continuous on each $I_j$.
\end{corollary}

% \begin{corollary}[Curve Selection]
%   Let $F$ be a real closed field.
%   Let $X \subseteq F^n$ be semialgebraic and $\overline{a}$
%   be a point in the closure of $X$.
%   There is a continuous semialgebraic function $f:(0,r) \to F^n$
%   such that for all $\epsilon\in(0,r)$, $f(x) \in X$ and $\lim_{\epsilon\to 0} f(\epsilon) = \overline{a}$.
% \end{corollary}

\begin{corollary}
  Let $F$ be a real closed field.
  Let $E \subseteq F^n \times F^n$ be a definable equivalence relation.
  There is a definable $X \subset F^n$ such that for all
  $a \in F^n$ there is a unique $b\in X$ such that $aEb$.
  Such $X$ is called a definable \emph{transversal} of $E$.
\end{corollary}

\begin{definition}[Cell]
  Inductive definition of the collection of \emph{cells}.
  \begin{enumerate}[label = {$\bullet$}]
    \item $X \subseteq F^n$ is a $0$-cell if it is a single point.
    \item $X \subset F$ is a $1$-cell if it is an interval $(a,b)$,
      where $a \in F \cup \{-\infty\}$, $b\in F\cup \{+\infty\}$, and $a < b$.
    \item If $X \subset F^n$ is an $n$-cell and $f: X\to F$ is a continuous definable function,
      then $Y = \{(\overline{x},f(\overline{x})): \overline{x} \in X\}$ is an $n$-cell.
    \item Let $X \subseteq F^n$ be an $n$-cell. Suppose that $f$ is
      either a continuous definable function from $X$ to $F$ or identically $-\infty$ and
      $g$ is either a continuous definable function from $X$ to $F$
      such that $f(\overline{x}) < g(\overline{x})$ for all $\overline{x} \in X$ or identically $+infty$, then
      \[
        Y = \{(\overline{x},y): \overline{x} \in X \land f(\overline{x}) < y < g(\overline{x})\}
      \]
      is an $n+1$-cell.
  \end{enumerate}
\end{definition}

% \begin{lemma}
%   Let $X \subseteq F^{n+1}$ be semialgebraic.
%   There is a natural number $N$ such that if $\overline{a}\in F^n$
%   and $X_{\overline{a}} = \{y: (\overline{a},y)\in X\}$ is finite,
%   then $|X_{\overline{a}}| < N$.
% \end{lemma}

\begin{tcolorbox}[title = {Cell Decomposition}]
\begin{theorem}
  Let $X \subseteq F^m$ be semialgebraic.
  There are finitely many pairwise disjoint cells $C_1,\dots,C_n$ such that $X = C_1 \cup \dots \cup C_n$.
\end{theorem}
\end{tcolorbox}

\begin{theorem}[Real Nullstellensatz]
  Let $F$ be a real closed field,
  and let $I$ be an ideal in $F[\overline{X}]$.
  Then, $V_F(I)$ is nonempty if and only if whenever $p_1,\dots,p_m\in F[\overline{X}]$ and $\sum p_i^2 \in I$,
  then all the $p_i \in I$.
\end{theorem}

Let $\mathbb{R}_{\exp} = (\mathbb{R},+,\cdot,\exp,<,0,1)$.

\begin{theorem}
  The theory of $\mathbb{R}_{\exp}$ is model-complete and o-minimal.
\end{theorem}

% \subsubsection{van den Dries's original statements}

% We work with a fixed but arbitrary o-minimal structure $(R,<,\mathcal{S})$.

% \begin{theorem}[Monotonicity Theorem]
%     Let $f: (a,b)\to R$ be a definable function on the interval $(a,b)$.
%     Then there are points $a_1 < \cdot < a_k$ in $(a,b)$ such that on each subinterval $(a_j,a_{j+1})$,
%     with $a_0 = a$, $a_{k+1} = b$,
%     the function is either constant, or strictly monotone and continuous.
% \end{theorem}

% \begin{corollary}
%     Let $f: (a,b) \to R$ be definable.
%     Then for each $c\in (a,b)$ the limit $\lim_{x\uparrow c}f(x)$
%     and $\lim_{x\downarrow c}f(x)$ exist in $R_{\infty}$.
%     Also the limits $\lim_{x\uparrow b}f(x)$ and $\lim_{x\downarrow a}f(x)$ exist in $R_{\infty}$.
% \end{corollary}

% \begin{corollary}
%     Let $f: [a,b]\to R$ be continuous and definable.
%     Then $f$ takes a maximum and a minimum value on $[a,b]$.
% \end{corollary}

% \begin{lemma}[Finiteness Lemma]
%     Let $A \subset R^2$ be definable and suppose that for each $x\in R$
%     the fiber $A_x \coloneq \{y\in R\colon (x,y)\in A\}$ is finite.
%     Then there is $N \in \mathbb{N}$ such that $A_x \le N$ for all $x\in R$.
% \end{lemma}

% A decomposition $\mathcal{D}$ of $R^m$ is said to \textbf{partition}
% a set $S \subseteq R^m$ if each cell in $\mathcal{D}$ is
% either part of $S$ or disjoint from $S$,
% in other words, if $S$ is a union of cells in $\mathcal{D}$.
% \begin{theorem}[Cell Decomposition]
%     \hfill
%     \begin{enumerate}[label = {$\mathrm{(\Roman*_{m})}$}]
%         \item Given any definable sets $A_1,dots,A_k \subset R^m$ there is a decomposition of $R^m$ partitioning each of $A_1,\dots,A_k$.
%         \item For each definable function $f: A \to R$, $A \subseteq R^m$,
%         there is a decomposition $\mathcal{D}$ of $R^m$ partitioning $A$ such that
%         the restriction $f|B: B \to R$ to each cell $B \in \mathcal{D}$ with $B \subseteq A$ is continuous.
%     \end{enumerate}
% \end{theorem}

% \begin{theorem}
%     The theory $\mathbb{R}_{\exp}$ is model-complete and o-minimal.
% \end{theorem}

% \subsubsection{}
% \begin{theorem}
%   Let $(R,<,\mathcal{S})$ be an o-minimal structure and
%   $S \subseteq R^{p+q}$ a definable set.
%   Then there is a positive integer $d = d(S)$ such that
%   for all sufficiently large $n\in\mathbb{N}$
%   each $n$-element set $F \subseteq R^q$ has at most $n^d$ subsets of the form $S_x \cap F$ with $x \in R^p$.
% \end{theorem}

% Let $\mathcal{C}$ be a collection of subsets of an infinite set $X$.
% Given $F \subseteq X$,
%   \[
%     \mathcal{C}\cap F := \{\mathcal{C}\cap F:C \in \mathcal{C}\},
%   \]
% the set of intersections of sets in $\mathcal{C}$ with $F$.
%   If $A \subseteq F$ is of the form $A = C\cap F$ for some $C\in \mathcal{C}$,
%   $A$ is \emph{cut out from $F$ by a set in $\mathcal{C}$}.
%   \[
%     f_{\mathcal{C}}(n):=\max\{|\mathcal{C}\cap F|:F\text{ is an $n$-element subset of $X$}\}.
%   \]

% \begin{theorem}
%   Either $f_{\mathcal{C}}(n) = 2^n$ for all $n$,
%   or else there is $d\in \mathbb{N}$ such that
%   $f_{\mathcal{C}}(n) = n^d$ for all sufficiently large $n$.
% \end{theorem}

% \begin{theorem}
%   Let $\mathcal{R} = (R,\dots)$ be an infinite model-theoretic structure and suppose
%   all definable relations $\Phi \subseteq R^p \times R$ for all $p > 0$, and dependent.
%   Then all definable relations $\Phi \subseteq R^p \times R^q$,
%   for all $p$, $q > 0$, are dependent.
% \end{theorem}

% \begin{theorem}[Ramsey's Theorem]
%   Given positive integers $M$, $r$ and $k$,
%   there is a positive integer $N = N(M,r,k)$ so large that
%   if $X$ is a set with $|X| \ge N$ and
%   $X^{(r)} = P_1 \cup P_2 \cup \dots \cup P_k$,
%   then there is a set $Y \subseteq X$ with $|Y|=M$ such that
%   $Y^{(r)} \subseteq P_j$ for some $j\in \{1,\dots,k\}$.
% \end{theorem}

% \begin{definition}
%   Let $X$ be an infinite set.
%   Given a relation $A \subseteq X^r$,
%   a finite sequence $x_1,\dots,x_M$ in $X$ is \emph{$A$-indiscernible} if
%   \[
%     (x_{i(1)},\dots,x_{i(r)})\in A \iff (x_{j(1)},\dots,x_{j(r)}) \in A.
%   \]
%   whenever $1\le i(1) < \cdots < i(r) \le M$ and
%   $1\le j(1) < \cdots < j(r) \le M$.
%   Let $\mathcal{A}$ be a collection of relations on $X$,
%   that is, each element of $\mathcal{A}$ is a set $A \subseteq A^r$,
%   with $r \in\mathbb{N}$ depending on $A$.
%   Then a sequence $x_1,\dots,x_M$ in $X$ is called \emph{$\mathcal{A}$-indiscernible} if it is $A$-indiscernible for each $A \in \mathcal{A}$.
%   A \emph{subsequence} of a sequence $x_1,\dots,x_N$ is by definition a sequence $x_{i(1)},\dots,x_{i(M)}$ with
%   $1\le i(1)< \dots < i(M) \le N$.
% \end{definition}

% \begin{corollary}
%     Let $X$ be an infinite set and $\mathcal{A}$ a finite collection of relation on $X$.
%     Then, given any positive integer $M$ there is a positive integer $N$ so large that each sequence in $X$ of length $N$ contains an $\mathcal{A}$-indiscernible subsequence of length $M$.
% \end{corollary}

% TODO

% \subsubsection{}
% Fix an o-minimal expansion $(R,<,\mathcal{S})$ of an ordered abelian group $(R,<,0,-,+)$.

% Definable curves play a role similar to that of sequences in $\mathbb{R}$, better properties.

% \begin{corollary}[Curve Selection]
%     If $a\in\mathrm{cl}(X)-X$,
%     where $X$ is definable,
%     then there is a definable continuous injective map
%     $\gamma: (0,\epsilon) \to X$, for some $\epsilon > 0$,
%     such that $\lim_{t\to 0}\gamma(t) = a$.
% \end{corollary}

% \begin{lemma}
%     Let $f: X \to R^n$ be a definable continuous map on a closed bounded set $X \subseteq R^m$.
%     Then $f(X)$ is bounded in $R^n$.
% \end{lemma}

% \begin{proposition}
%     If $f: X \to R^n$ is a continuous definable map on a closed bounded set $X \subseteq R^m$,
%     then $f(X)$ is closed and bounded in $R^m$.
% \end{proposition}

% TODO

% \subsubsection{}
% \begin{theorem}[Triangulation Theorem]
%     Let $S \subset R^m$ be a definable set,
%     with definable subsets $S_1,\dots,S_k$.
%     Then $S$ has a triangulation in $R^m$ that is compatible with these subsets.
% \end{theorem}

% TODO

\subsection{About Types}
Suppose that $\mathcal{M}$ is an $\mathcal{L}$-structure and $A \subseteq M$.
Let $\mathcal{L}_A$ be the language obtained by adding to $\mathcal{L}$ constant symbols for each $a\in A$.
We can naturally view $\mathcal{M}$ as an $\mathcal{L}_A$-structure by interpreting the new symbols in the obvious way.
Let $\mathrm{Th}_A(\mathcal{M})$ be the set of all $\mathcal{L}_A$-sentences true in $\mathcal{M}$.
% Note that $\mathrm{Th}_A(\mathcal{M}) \subseteq \mathrm{Diag_el}(\mathcal{M})$.

\begin{definition}
  Let $p$ be the set of $\mathcal{L}_A$-formulas in free variables $v_1,\dots,v_n$.
  $p$ is an \emph{$n$-type} if $p\cup \mathrm{Th}_A(\mathcal{M})$ is satisfiable.
  $p$ is a \emph{complete $n$-type} if $\phi\in p$ or $\neg\phi\in p$ for all $\mathcal{L}_A$-formulas $\phi$ with free variables from $v_1,\dots,v_n$.
  Let $S^{\mathcal{M}}_n(A)$ be the set of all complete $n$-types.

  Incomplete types are referred to as \emph{partial types}.
  We often write $p(v_1,\dots,v_n)$ to stress that $p$ is an $n$-type.

  If $\mathcal{M}$ is any $\mathcal{L}$-structure,
  $A \subset M$, and $(a_1,\dots,a_n)\in M^n$,
  let $\mathrm{tp}^{\mathcal{M}}(\overline{a}/A) = \{\phi(v_1,\dots,v_m)\in \mathcal{L}_A:\mathcal{M}\models \phi(a_1,\dots,a_n)\}$.
  Then, $\mathrm{tp}^{\mathcal{M}}(\overline{a}/A)$ is a complete $n$-type.
  Write $\mathrm{tp}^{\mathcal{M}}(\overline{a})$ for $\mathrm{tp}^{\mathcal{M}}(\overline{a}/\emptyset)$.

  If $p$ is an $n$-type over $A$,
  $\overline{a}\in M^n$ \emph{realizes $p$} if $\mathcal{M} \models \phi(\overline{a})$ for all $\phi\in p$.
  If $p$ is not realized in $\mathcal{M}$,
  then $\mathcal{M}$ \emph{omits $p$}.
\end{definition}

\begin{definition}
  Let $T$ be a complete theory in a countable language,
  and let $\kappa$ be an infinite cardinal.
  $T$ is \emph{$\kappa$-stable} if whenever $\mathcal{M}\models T$,
  $A \subseteq M$, and $|A| = \kappa$, then $|S^{\mathcal{M}}_n(A)| = \kappa$.
\end{definition}

\begin{definition}
  Let $\phi(v_1,\dots,v_n)$ be an $\mathcal{L}$-formula such that $T \cup \{\phi(\overline{v})\}$ is satisfiable,
  and let $p$ be an $n$-type.
  \emph{$\phi$ isolates $p$} if
  \[
    T \models \forall\overline{v}(\phi(\overline{v}) \to \psi(\overline{v}))
  \]
  for all $\psi \in p$.
\end{definition}
Note that if $p$ is a complete type and $\phi(\overline{v})$ isolates $p$, then
\[
  T \models \phi(\overline{v}) \to \psi(\overline{{v}}) \iff \psi(\overline{v})\in p
\]
for all formulas $\psi(\overline{v})$.
In particular, for all formulas $\psi(\overline{v})$,
exactly one of $T + \phi(\overline{v}) \land \psi(\overline{v})$ and $T + \phi(\overline{v}) \land \neg\psi(\overline{v})$ is satisfiable.

\begin{theorem}[Omitting Types Theorem]
  Let $\mathcal{L}$ be a countable language,
  $T$ an $\mathcal{L}$-theory,
  and $p$ a (possibly incomplete) non-isolated $n$-type over $\emptyset$.
  Then, there is a countable $\mathcal{M} \models T$ omitting $p$.
\end{theorem}

\begin{definition}
  $\mathcal{M}\models T$ is a \emph{prime model} of $T$ if whenever $\mathcal{N}\models T$ there is an elementary embedding of $\mathcal{M}$ into $\mathcal{N}$.
\end{definition}

\begin{definition}
  $\mathcal{M}\models T$ is \emph{atomic} if $\mathrm{tp}^{\mathcal{M}}(\overline{a})$ is isolated for all $\overline{a} \in M^n$.
\end{definition}

\begin{definition}
  Let $\kappa$ be an infinite cardinal.
  $\mathcal{M}\models T$ is \emph{$\kappa$-homogeneous}
  if whenever $A \subset M$ with $|A| < \kappa$,
  $f: A \to M$ is a partial elementary map,
  and $a \in M$, there is $f^*\supseteq f$ such that $f^*: A\cup \{a\} \to M$ is partial elementary.

  $\mathcal{M}$ is \emph{homogeneous} if it is $|M|$-homogeneous.
\end{definition}

\begin{definition}
  Let $T$ be a complete theory in a countable language,
  and let $\kappa$ be an infinite cardinal.
  $T$ is \emph{$\kappa$-stable} if whenever $\mathcal{M}\models T$,
  $A \subseteq M$, and $|A| = \kappa$, then $|S^{\mathcal{M}}_n(A)| = \kappa$.

  $\mathcal{M}$ is $\kappa$-stable if $\mathrm{Th}(\mathcal{M})$ is $\kappa$-stable.
\end{definition}

\begin{definition}
  Let $\kappa$ be an infinite cardinal.
  $\mathcal{M} \models T$ is $\kappa$-saturated if,
  for all $A \subseteq M$, if $|A| < \kappa$ and $p \in S^{\mathcal{M}}_n(A)$,
  then $p$ is realized in $\mathcal{M}$.

  $\mathcal{M}$ is \emph{saturated} if it is $|M|$-saturated.
\end{definition}

\begin{proposition}
  If $\mathcal{M}$ is $\kappa$-saturated,
  then $\mathcal{M}$ is $\kappa$-homogeneous.
\end{proposition}

\begin{definition}
  $\mathcal{M} \models T$ is \emph{$\kappa$-universal} if for all $\mathcal{N}\models T$ with $|N| < \kappa$ there is an elementary embedding of $\mathcal{N}$ into $\mathcal{M}$.

  $\mathcal{M}$ is \emph{universal} if it is $|M|^+$-universal.
\end{definition}

\begin{theorem}
  Let $\kappa \ge \aleph_0$.
  The following are equivalent.
  \begin{enumerate}[label = {\roman*)}]
    \item $\mathcal{M}$ is $\kappa$-saturated.
    \item $\mathcal{M}$ is $\kappa$-homogeneous and $\kappa^+$-universal.
  \end{enumerate}
  If $\kappa \ge \aleph_1$, i) and ii) are also equivalent to:
  \begin{enumerate}[resume, label = {\roman*)}]
    \item $\mathcal{M}$ is $\kappa$-homogeneous and $\kappa$-universal.
  \end{enumerate}
\end{theorem}

\begin{corollary}
  $\mathcal{M}$ is saturated if and only if it is homogeneous and universal.
\end{corollary}

\begin{theorem}
  If $\mathcal{M}$ and $\mathcal{N}$ are saturated models of $T$ of cardinality of $\kappa$,
  then $\mathcal{M}\cong\mathcal{N}$.
\end{theorem}

\begin{proposition}
  Let $\mathcal{M}$ be saturated.
  Let $A \subset M$ with $|A| < |M|$.
  Let $X \subset M^n$ be definable with parameters from $M$.
  Then, $X$ is $A$-definable if and only if every automorphism of $\mathcal{M}$ that fixes $A$ pointwise fixes the $X$ setwise.
\end{proposition}

$b \in M$ is \emph{definable from $A$} if $\{b\}$ is $A$-definable.
\begin{corollary}
  Let $\mathcal{M}$ be saturated,
  and let $A \subset M$ with $|A| < |M|$.
  Then, $b$ is definable from $A$ if and only if $b$ is fixed by all automorphisms of $\mathcal{M}$ that fix $A$ pointwise.
\end{corollary}

$b$ is \emph{algebraic} over $A$ if there is a finite $A$-definable set $X$ such that $b\in X$.
\begin{proposition}
  Let $\mathcal{M}$ be saturated.
  Let $A \subset M$ with $|A| < |M|$ and $b \in M$.
  The following are equivalent:
  \begin{enumerate}[label = {\roman*)}]
    \item $b$ is algebraic over $A$;
    \item $b$ has only finitely many images under automorphisms of $\mathcal{M}$ fixing $A$ pointwise;
    \item $\mathrm{tp}^{\mathcal{M}}(b/A)$ has finitely many realization.
  \end{enumerate}
\end{proposition}

\subsection{Definable Spaces and Quotients}
\subsubsection{Definable spaces}
Let a covering $S = \bigcup_i U_i$ of a set $S$ by subsets $U_i$ ($i\in I$) be given,
and for each index $i \in I$ a set-theoretic bijection $g_i: U_i \to U'_i$ a topological space,
such that the transition maps are continuous.

Suppose that the index set $I$ is finite,
that each $U'_i \subseteq R^{m(i)}$ is a definable set,
and for each pair $i$, $j$ the set $g_i(U_i\cap U_j) \subseteq U'_i$
is definable and $g_{ij}: g_i(U_i\cap U_j) \to g_j(U_j\cap U_i)$ is definable.
(Such a family is called a \emph{definable atlas of $S$}.)

Let $X \subseteq S$ and $f : X \to R$;
call $X$ \emph{definable} if $g_i(X\cup U_i) \subseteq I'_i$ is definable for each $i$,
and call $f$ \emph{definable} if $X$ is definable and
$f_i : g_i(X \cap U_i) \to R$ given by $f_i(x) = f(g_i^{-1}(x))$ is definable for each $i$.
If $X = X_1\cup \cdots \cup X_n$,
where all $X_k$ are definable,
then a function $f: X \to R$ is definable if and only if each restriction $f|X_k: X_k \to R$ is definable.

Note that $U_i$ is definable,
and for $g_i = (g_{i1},\dots,g_{im(i)}) : U_i \to R^{m(i)}$,
each $g_{ik}$ is definable.
Let $\mathbf{DO}(S)$ be the collection of definable open subsets of $S$,
and for each $U \in \mathbf{DO}(S)$,
let $\mathbf{DC}(U)$ be the $R$-algebra of definable continuous functions $f: U \to R$.
Then we call the set $S$ equipped with the sheaf $(\mathbf{DC}(U))_{U \in \mathbf{DO}(S)}$ a \emph{definable space}.

\begin{definition}
  Let $S$ and $T$ be definable spaces.
  Then a map $F: S \to T$ is said to be \emph{definable} if its graph $\Gamma(F)$ is a definable subset of
  the product space $S \times T$.
\end{definition}

\begin{definition}
  Recall that a topological space $S$ is said to be regular if for each $a \in  S$ and
  open $U \subseteq S$ with $a \in U$ there is an open $V \subseteq S$ with $a \in V$ and $\mathrm{cl}(V) \subseteq U$.
  A definable space $S$ is regular if and only if for each $a \in S$ and definable open $U \subseteq S$ with $a \in U$
  there is a definable open $V \subseteq S$ with $a \in V$ and $\mathrm{cl}(V) \subseteq U$,
  and also if and only if for each $a \in S$ and definable closed $X \subseteq S$ with $a \notin X$
  there are disjoint definable open neighborhoods of $a$ and $X$ in $S$.
\end{definition}

\subsubsection{Definable quotient spaces}

Let $E \subseteq X\times X$ be a definable equivalence relation on a definable set $X \subseteq R^m$.

\begin{definition}
  A \emph{definable quotient of $X$ be $E$} is a pair $(p,Y)$ consisting of a definable set $Y \subseteq R^n$ and definable continuous surjective map $p: X\to Y$ such that
  \begin{enumerate}[label = {(\roman*)}]
    \item $E = E_p$, i.e., $(x_1,x_2) \in E \iff p(x_1) = p(x_2)$ for all $x_1$, $x_2 \in X$;
    \item $p$ is definably identifying, i.e., for all definable $K \subseteq Y$, if $p^{-1}(K)$ is closed in $X$, then $K$ is closed in $Y$.
  \end{enumerate}
\end{definition}

Let $E$ be a definable equivalence relation on a definable set $X$.
Let $pr_1 : E \to X$ and $pr_2 : E \to X$ be the restrictions of the two projection maps $X\times X \to X$.

$E$ is called \emph{definably proper over $X$} if $pr_1$ is a definably proper map.

\begin{theorem}
  Suppose the definable equivalence relation $E$ on the definable set $X$ is definably proper over $X$.
  Then $X/E$ exists as a definably proper quotient of $X$.
\end{theorem}

\section{Definable complex geometry}
Materials follow from \cite{MR2441378}.

Let $\mathbf{R}$ be a real closed field and $\mathbf{K}$ its algebraic closure,
identified with $\mathbf{R}^2$ (after fixing a square-root of $-1$).

\subsection{Topological aspects}

\begin{definition}
  A \emph{definable $C^0$ $\mathbf{R}$-manifold of dimension $n$, with respect to $\mathbf{R}$} is a set $X$,
  covered by finitely many nonempty sets $U_1, \dots, U_k$,
  and for each $i = 1, \dots, k$,
  there is a set-theoretic bijection $\phi_i:U_i \to V_i$,
  where $V_i$ is definable and open in $\mathbf{R}^n$ and such that each $\phi_i(U_j\cap U_i)$ is definable an open
  and the transition maps are definable and continuous.
  Moreover, the topology induced on $X$ by this covering is Hausdorff.

  A manifold is a \emph{$C^p$ $\mathbf{R}$-manifold} if in addition
  the transition maps are $C^p$ with respect to the field $\mathbf{R}$.
\end{definition}

\begin{definition}
  Let $X$ be a definable subset of $\mathbf{R}^n$.
  $X$ is called \emph{definably compact} if for every definable continuous $\gamma:(0,1) \to X$ the limit of $\gamma(t)$,
  as $t$ tends to $0$ in $\mathbf{R}$, exists in $X$.
  This is equivalent to $X$ being closed and bounded in $\mathbf{R}^n$.

  A definable set $X \subseteq \mathbf{R}^n$ is \emph{locally definably compact}
  if every $x \in $ has a definable neighborhood $V\subseteq X$
  (i.e., $V$ contains an $X$-open set around $x$)
  which is definably compact.

  $X \subseteq \mathbf{R}^n$ is \emph{locally closed} if there is a (definable) open set $U \subseteq \mathbf{R}^n$ containing $X$
  such that $X$ is relatively closed in $U$.

  Let $U$ be an open subset of $\mathbf{R}^n$.
  For $X \subseteq U$,
  the \emph{frontier of $X$ in $U$} is defined as $Fr_U(X) = Cl_U(X)\backslash X$,
  where $Cl_U(X)$ is the closure of $X$ in $U$.
  If $U = \mathbf{R}^n$ then we write $Fr(X)$ instead of $Fr_{\mathbf{R}^n}$.
\end{definition}

\begin{lemma}
  Let $X$ be a definable subset of $\mathbf{R}^n$.
  Then the following are equivalent:
  \begin{enumerate}[label = {(\roman*)}]
    \item $X$ is locally definably compact.
    \item $X$ is locally closed in $\mathbf{R}^n$.
    \item $Fr(X)$ is closed subset of $\mathbf{R}^n$.
  \end{enumerate}
\end{lemma}

\begin{definition}
  Let $f$ be a definable continuous map from a definable $X \subseteq \mathbf{R}^n$ into $Y \subseteq \mathbf{R}^k$.

  For $b \in Y$, $f$ is \emph{definably proper over $b$} if for every definable curve $\gamma:(0,1) \to X$ such that $\lim_{t\to 0} f(\gamma(t)) = b$,
  $\gamma(t)$ tends to some limit in $X$ as $t$ tends to $0$.
  If $f: X \to Y$ is definably proper over every $b\in Y$ then
  we say that $f$ is \emph{definably proper over $Y$} or just
  $f$ is \emph{definably proper}.

  For $A \subseteq X$, we say that $f|A$ is \emph{definably proper over its image} if $f|A : A \to f(A)$ is definably proper over $f(A)$.

  We say that $f$ is \emph{bounded over $b\in Y$} if there is a neighborhood $W \subseteq Y$ of $b$ such that $f^{-1}(W)$ is bounded subset of $\mathbf{R}^n$.
\end{definition}

% \begin{lemma}
%   For $f: X \to Y$ a definable continuous map,
%   $X \subseteq \mathbf{R}^n$,
%   and $y\in Y$, the following are equivalent:
%   \begin{enumerate}[label = {(\roman*)}]
%     \item $f$ is definably proper over $y$.
%     \item $f$ is bounded over $y$ and the intersection of the closure of the graph of $f$
%       in $\mathbf{R}^n\times Y$ with $Fr(X)\times \{y\}$ is empty.
%   \end{enumerate}
% \end{lemma}

% \begin{lemma}
%   Let $X \subseteq \mathbf{R}^n$ be a definable,
%   locally closed set, $f: X \to \mathbf{R}^k$ a definable
%   continuous map. Then,
%   \begin{enumerate}[label = {(\roman*)}]
%     \item The set of all $y \in \mathbf{R}^k$ such that $f$ is definably proper over $y$ is open in $\mathbf{R}^k$.
%     \item If $f$ is definably proper over $f(X)$, then $f(X)$ is locally closed set.
%   \end{enumerate}
% \end{lemma}

Assume that the structure is $\omega_1$-saturated if generic points are mentioned.

\begin{definition}
  Let $H \subseteq \mathbf{K}^n$ be a $d$-dimensional $\mathbf{K}$-subspace of $\mathbf{K}^n$.
  $H$ is \emph{generic over a set $C \subseteq \mathbf{R}$} if the following holds:
  Let $\{H_s: s \in S\}$ be some $C$-definable parametrization of all $d$-dimensional $\mathbf{K}$-linear subspaces of $\mathbf{K}^n$.
  Then $H = H_s$ for some $s$ generic in $S$ over $C$.
\end{definition}

For $H$ a $d$-dimensional $\mathbf{K}$-subspace of $\mathbf{K}^n$,
an orthogonal projection $\pi:\mathbf{K}^n \to H$ is \emph{generic over $C$} if $H$ is generic over $C$.

\begin{definition}
  A definable subset $A$ of $\mathbf{R}^k$ is called an $m$-dimensional $C^p$ $\mathbf{R}$-submanifold of $\mathbf{R}^k$
  if for every $x\in A$ there is a definable open neighborhood $U$ of $x$ and definable $C^p$ (with respect to $\mathbf{R}$) map
  $f: U \to \mathbf{R}^{n-m}$ such that $A \cap U = f^{-1}(0)$ and the rank of the $\mathbf{R}$-differential $df_x$ of $f$ at $x$ equals $n-m$.
\end{definition}

In classical complex analytic geometry,
given a complex analytic set $A$ and $p \in A$,
one moves to a local coordinates system,
chosen properly, in order to ensure that the projection map from $A$ onto (some of) the coordinates is a proper map in this neighborhood.
The following theorem is probably the most significant advantage of the o-minimal setting in comparison with the general classical setting.
It allows us to work globally rather than locally.

\begin{tcolorbox}[title = {The main covering theorem}]
\begin{theorem}
  Let $A$ be a definable, locally closed subset of $\mathbf{K}^n$,
  such that $\dim_{\mathbf{R}}A = 2d < 2n$.

  Then there are definable open sets $U_1,\dots,U_k \subseteq \mathbf{K}^n$ and $d$-dimensional $\mathbf{K}$-linear subspaces $L_1,\dots,L_k$ such that
  \begin{enumerate}[label = {(\arabic*)}]
    \item $\bigcup_{i=1}^k U_i = \mathbf{K}^n\backslash Fr_{\mathbf{K}^n}(A)$ (in partition $A$ is contained in the union of the $U_i$'s).
    \item For each $i = 1,\dots,k$, if $\pi_i:\mathbf{K}^n \to L_i$ is the orthogonal projection, then $\pi_i|U_i\cap A$ is definably proper over $\pi_i(U_i)$.
    \item If furthermore $A$ is a $C^1$ $\mathbf{R}$-submanifold of $\mathbf{K}^n$ then the $U_i$'s and $L_i$'s can be chosen to satisfy also:
    For every $i=1,\dots,k$ the map $\pi_1|A\cap U_i$ is local diffeomorphism and there is $m = m_i$ such that every $y \in \pi_i(U_i)$ has exactly $m$ pre-images under $\pi_i$ in $A \cap U_i$.
  \end{enumerate}
\end{theorem}
\end{tcolorbox}

\subsection{Analytic aspects}
For $U \subseteq \mathbf{K}$ a definable open set and $z_0 \in U$,
a definable function $f: U \to \mathbf{K}$ is \emph{$\mathbf{K}$-differentiable at $z_0$} if $\lim_{h\to 0}(f(z_0+h) - f(z_0))/h$ exists in $\mathbf{K}$.
If $f$ is $\mathbf{K}$-differentiable at every point on $U$ then
$f$ is \emph{$\mathbf{K}$-holomorphic in $U$}.

\begin{definition}
  A \emph{$d$-dimensional $\mathbf{K}$-manifold} is a set $X$,
  together with a finite cover $X = \bigcup_{i=1}^r U_i$,
  and for each $i = 1,\dots,r$ a set-theoretic bijection $\phi_i: U_i \to V_i$,
  with $V_i$ a definable subset open of $\mathbf{K}^d$,
  such that for each $i$, $j$,
  the set $\phi_i(U_i \cap U_j)$ is a definable open subset of $V_i$ and the transition maps $\phi_j \phi_i^{-1}$ are $\mathbf{K}$-holomorphic.
  Moreover, the naturally induced topology is Hausdorff.
\end{definition}

\begin{definition}
  Let $N$ be a $\mathbf{K}$-manifold.
  A definable $M \subseteq N$ is called a \emph{$d$-dimensional $\mathbf{K}$-submanifold of $N$} if for every $a\in M$ there is a definable open set $U \subseteq N$ containing $a$ and a $\mathbf{K}$-holomorphic $f: U \to \mathbf{K}^{n-d}$ such that $M \cup U = f^{-1}(0)$ and $\mathrm{rank}_{\mathbf{K}}(Df_a) = n-d$,
  where $Df_x$ is the $\mathbf{K}$-differential of $f$ at $x$.
\end{definition}

\begin{definition}
  If $A$ is a definable subset of a $\mathbf{K}$-manifold $M$,
  then $A$ is a \emph{locally $\mathbf{K}$-analytic subset} of $M$
  if for every $a\in A$ there is a definable open $V \subseteq M$ containing $a$ and a $\mathbf{K}$-holomorphic map $f : V \to \mathbf{K}^m$,
  for some $m$, such that $A\cap V= f^{-1}(0)$.
  A is called a \emph{$\mathbf{K}$-analytic subset} of $M$ if in addition to the above $A$ is closed in $M$.

  A definable closed $A \subseteq M$ is \emph{finitely $\mathbf{K}$-analytic subset} of $M$ if it can be covered by finitely many definable open subsets of $M$,
  on each of which $A$ is the zero set of some $\mathbf{K}$-holomorphic map.
  A $\mathbf{K}$-analytic subset $A $of $M$ is called \emph{reducible} if it can be written as $A= A_1 \cup A_2$,
  where $A_1$ and $A_2$ are $\mathbf{K}$-analytic in $M$ and none of the $A_i$'s is contained in the other.
  When $A$ is not reducible it is called \emph{irreducible}.
\end{definition}

\begin{theorem}
  Let $G \subseteq \mathbb{C}^n$ be an open set and let $X$ be a $\mathbb{C}$-analytic subset of $G$ such that both $X$ and $G$ are definable in $\mathbb{R}_{\exp}$.
  Then there is a complex algebraic set $A \subseteq \mathbb{C}^n$ such that $X$ is the union of several irreducible components of $A\cap G$.
\end{theorem}

\begin{definition}
  Let $N$ be a $\mathbf{K}$-manifold.
  If $A \subseteq N$ is an arbitrary definable set then $\mathrm{Reg}_{\mathbf{K}}A$ is the set of all points $z \in A$ such that in some neighborhood of $a$,
  the set $A$ is a $\mathbf{K}$-submanifold of $N$.
  We let $\mathrm{Sing}_{\mathbf{K}}A = A \backslash \mathrm{Reg}_{\mathbf{K}}A$.
\end{definition}

\begin{lemma}
  If $A$ is a $\mathbf{K}$-analytic subset of a $\mathbf{K}$-manifold $N$ and $\mathrm{Reg}_{\mathbf{K}}A$ is definably connected then $A$ is irreducible.
  In particular, the number of irreducible components of $A$ is finite.
\end{lemma}

\begin{lemma}
  Let $U$ be a definable open subset of $\mathbf{K}^n$,
  $A$ a definable relatively closed subset of $U$
  whose $\mathbf{R}$-dimension is $2d$.
  Assume that $\mathrm{Reg}_{\mathbf{K}}A$ is definably connected,
  dense in $A$, and that $\dim_{\mathbf{R}}(\mathrm{Sing}_{\mathbf{K}}A) \le 2d-2$.
  Assume also that the projection map onto the first $d$ coordinates,
  $\pi : A \to \mathbf{K}^d$,
  is finite-to-one and definably proper over its image.

  Then, $\pi(A)$ is open in $\mathbf{K}^d$ and there is an $r\in \mathbb{N}$ and a $\mathbf{K}$-holomorphic map
  $\Psi: \pi(A) \times \mathbf{K}^{n-d} \to \mathbf{K}^d$ such that $A$ is the zero set of $\Psi$.

  Moreover, the map $\Psi$ can be definably recovered in the structure $(\mathbf{R},<,+,\cdot,A)$.
\end{lemma}

\begin{tcolorbox}
\begin{theorem}
  Let $M$ ba $\mathbf{K}$-manifold and $A$ a definable closed subset of $M$.
  Assume that for every open $U \subseteq M$,
  $\dim_{\mathbf{R}}(\mathrm{Sing}_{\mathbf{K}}(A\cap U)) \le \dim_{\mathbf{R}}(A\cap U) -2$.
  Then $A$ is a finitely $\mathbf{K}$-analytic subset of $M$.

  In particular, every $\mathbf{K}$-analytic subset of $M$ is finitely $\mathbf{K}$-analytic.
\end{theorem}
\end{tcolorbox}

\begin{corollary}
If $M$ is a $\mathbf{K}$-manifold and $A$ a closed definable subset of $M$ then the following are equivalent:
\begin{enumerate}[label = (\roman*)]
  \item For every open $W \subseteq \mathbf{K}^n$, $\dim_{\mathbf{R}}(\mathrm{Sing}_{\mathbf{K}}(A\cap W)) \le \dim_{\mathbf{R}}(A\cap W) -2$.
  \item $A$ is $\mathbf{K}$-analytic subset of $M$.
  \item $A$ is finitely $\mathbf{K}$-analytic subset of $M$.
\end{enumerate}
Moreover, in (iii) the open sets and $\mathbf{K}$-holomorphic functions which carve $A$ in each of them can be chosen be definable in the structure $(R,<,+,\cdot,A)$.
\end{corollary}

\begin{tcolorbox}[title = {Definable Chow's Theorem}]
\begin{theorem}
  Let $A$ be a definable $\mathbf{K}$-algebraic subset of $\mathbf{K}^n$.
  Then $A$ is an algebraic set over $\mathbf{K}$.
\end{theorem}
\end{tcolorbox}

\begin{corollary}
  Every bounded $\mathbf{K}$-analytic subset of $\mathbf{K}^n$ is finite.
\end{corollary}

\begin{tcolorbox}
  \begin{theorem}
    Let $M$ be a $\mathbf{K}$-manifold and let $A$ be a $\mathbf{K}$-analytic subset of $M$.
    Then $\mathrm{Sing}_{\mathbf{K}}(A)$ is a $\mathbf{K}$-analytic subset of $M$.
  \end{theorem}
\end{tcolorbox}

\begin{theorem}
  Assume that $A \subseteq U \subseteq \mathbf{K}^n$ is a $\mathbf{K}$-analytic set and $f: U \to \mathbf{K}^d$ is $\mathbf{K}$-holomorphic.
  Then the map $x\mapsto \dim_{\mathbf{K}}(A\cap f^{-1}(f(x)))_x$ is upper semi-continuous on $A$.
\end{theorem}

\begin{theorem}[The Dimension Theorem]
  Let $M$ be an $n$-dimensional \hspace{0em}
  $\mathbf{K}$-manifold,
  $X$, $Y$ definable, irreducible $\mathbf{K}$-analytic subsets of $M$.
  Then every irreducible component of $X \cap Y$ has $\mathbf{K}$-dimension not less than $\dim_{\mathbf{K}}X + \dim_{\mathbf{K}}Y - n$.
\end{theorem}

\begin{theorem}[Remmert's Proper Mapping Theorem]
  Let $f: M \to N$ be a $\mathbf{K}$-holomorphic map between $\mathbf{K}$-manifolds.
  Let $A \subseteq M$ be a $\mathbf{K}$-analytic subset.
  Assume that $f(A)$ is a closed subset of $N$.
  Then $f(A)$ is a $\mathbf{K}$-analytic subset of $N$.
\end{theorem}

\subsubsection{Zariski structures}

Classical complex manifold version:
\begin{theorem}[{\cite{zbMATH00554994}}]
  Consider the structure whose universe is a compact complex manifold,
  and whose atomic relations are all the complex analytic subsets of $M$ and of its Cartesian products.
  Then the structure eliminates quantifiers,
  it is stable of finite Morley Rank and moreover,
  it is a Zariski structure
  (with the closed sets taken as the K-analytic ones).
\end{theorem}

Model theoretic version:
\begin{theorem}
  Let $M$ be a definably compact $\mathbf{K}$-manifold,
  equipped with all $\mathbf{K}$-analytic subsets of Cartesian prodcuts of $M$.
  Then $M$ eleminates quantifiers,
  it is stable of finite Morley rank and a (complete) Zariski structure
  (with the closed sets taken as the $\mathbf{K}$-analytic ones).
\end{theorem}

\subsection{Applications}
\subsubsection{Meromorphic}
Let $M$, $N$ be $\mathbf{K}$-manifolds,
$U$ a definable open subset of $M$
whose complement is a $\mathbf{K}$-analytic subset of $M$.
A $\mathbf{K}$-holomorphic map $f: U \to N$ is
\emph{$\mathbf{K}$-meromorphic} if the closure of its graph in $M \times N$
is a $\mathbf{K}$-analytic subset of $M \times N$.

\begin{corollary}
  Let $M$, $N$ be $\mathbf{K}$-manifolds,
  $S \subseteq M$ an irreducible $\mathbf{K}$-analytic subset of $M$,
  and assume that $L$ is a closed definable subset of $S$ which contains $\mathrm{Sing}_{\mathbf{K}}S$.
  If $f: S \backslash L \to N$ is a $\mathbf{K}$-holomorphic map and
  $\dim_{\mathbf{R}}L \ge \dim_{\mathbf{R}}S -2$ then
  the closure of the graph of $f$ in $M \times N$ is a $\mathbf{K}$-analytic subset of $M \times N$.
\end{corollary}

\subsubsection{Campana--Fujiki}
\begin{definition}
  Let $M$ be a $\mathbf{K}$-manifold,
  a \emph{$\mathbf{K}$-holomorphic-vector-bundle over $M$,
  of dimension $d$} consists of a $\mathbf{K}$-manifold,
  a $\mathbf{K}$-holomorphic map $\rho: X \to M$,
  such that :

  There is finite cover of $M$ by definable open sets $M = \bigcup_{i=1}^k V_i$,
  and for each $i = 1,\dots,k$ there is a $\mathbf{K}$-biholomorphism
  $\phi_i: V \times \mathbf{K}^d \to \rho^{-1}(V_i)$ such that $\rho\phi_i(x,y) = x$.
  Furthermore, if $x \in V_i\cap V_j \neq\emptyset$ then $\phi_i^{-1}\phi_j$ induces
  a $\mathbf{K}$-linear automorphism $g_{i,j}(x)$ of the vector space $\mathbf{K}^d$,
  in the fiber above $x$.
  The map $x\mapsto g_{i,j}(x)$ is $\mathbf{K}$-holomorphic from $V_i\cap V_j$ into $\mathrm{GL}(d_i,\mathbf{K})$.
\end{definition}

\begin{tcolorbox}
  \begin{theorem}
    Assume that $N$, $M$ are $\mathbf{K}$-manifolds,
    and $S$ is an irreducible $\mathbf{K}$-analytic subset of $N \times M$.
    Then there is a $\mathbf{K}$-holomorphic vector-bundle
    $\pi: V \to M$, a $\mathbf{K}$-meromorphic map $\sigma: S \to \mathbb{P}(V)$,
    and a Zariski open subset $S^0$ of $S$ such that for all
    $(b,a)$, $(b',a)\in S^0$, $\sigma(b,a) = \sigma(b',a)$ if and only if
    $S_b = S_{b'}$ near $a$, and the following diagram of $\mathbf{K}$-meromorphic
    maps is commutative
    \[
      \begin{tikzcd}
        S^0 \ar[rr,"\sigma"]\ar[dr,"\pi_M"'] & & \mathbb{P}(V)\ar[dl,"\pi"] \\
        & M &
      \end{tikzcd}
      \]
  \end{theorem}
\end{tcolorbox}

\subsubsection{Fnite version of the Coherence Theorem}

Let $M$ be a $\mathbf{K}$-manifold of dimension $n$.
For $U \subseteq M$ a definable open set,
let $\mathcal{O}(U)$ denote the ring of $\mathbf{K}$-holomorphic functions on $U$.

For $p\in M$, denote by $\mathcal{O}_p$ the ring of germs at $p$ of $\mathbf{K}$-holomorphic functions.
When $M = \mathbf{K}^n$, sometimes write $\mathcal{O}_{n,p}$.
If $A$ is a $\mathbf{K}$-analytic subset of $M$,
and $p \in M$ then denote by $\mathcal{I}(A)_p$ the ideal in $\mathcal{O}_p$ of all germs at $p$ which vanish on $A$ in some neighborhood of $p$.
For a definable open $V \subseteq M$,
let $\mathcal{I}_V(A)$ be the set of all $\mathbf{K}$-holomorphic functions on $V$ which vanish on $A \cap V$;
this is a module over $\mathcal{O}(V)$.
When $A$ is a $\mathbf{K}$-analytic subset of $V$,
just write $\mathcal{I}(A)$ for $\mathcal{I}(A)_V$.

A function $f: A \to \mathbf{K}$ is called $\mathbf{K}$-holomorphic if there is an open definable set $V$, $A \subseteq V \subseteq U$,
and a $\mathbf{K}$-holomorphic function on $V$ which extends $f$.
For $p \in A$, denote $\mathcal{O}(A)_p$ the ring of germs at $p$ of $\mathbf{K}$-holomorphic functions on $A \cap W$ for some open neighborhood $W$ of $p$.
The ring $\mathcal{O}(A)_p$ can be identified with the quotient ring $\mathcal{O}_p/\mathcal{I}(A)_p$.

\begin{tcolorbox}[title = {Coherence Theorem}]
\begin{theorem}
  Let $M$ be a $\mathbf{K}$-manifold and $A \subseteq M$ a $\mathbf{K}$-analytic subset of $M$.
  Then there are finitely many open sets $V_1,\dots,V_k$ whose union covers $M$ and for each $i = 1,\dots,k$
  there are finitely many $\mathbf{K}$-holomorphic functions $f_{i,1},\dots,f_{i,m_i}$ in $\mathcal{I}_{V_i} (A)$,
  such that for every $p \in V_i$ the functions $f_{i,1},\dots,f_{i,m_i}$ generate the ideal $\mathcal{I}(A)_p$ in $\mathcal{O}_p$.

  Moreover, the $V_i$'s and the $f_{i,j}$'s are all definable over the same parameters defining $M$ and $A$.
\end{theorem}
\end{tcolorbox}

\subsubsection{Definable structures on complex number}
\begin{theorem}
  Assume that $M$ is an o-minimal structure expanding the field of real numbers such that every definable holomorphic function of $1$-variable is locally semialgebraic.

  Let $G \subseteq \mathbb{C}^n$ be a definable open set and $X$ a definable irreducible complex analytic subset of $G$.
  Then there is a complex algebraic set $A \subseteq \mathbb{C}^n$ such that $X$ is one of the irreducible components of $A \cap G$.
\end{theorem}

\begin{corollary}
  Let $X$ be an analytic subset of an open set $G\subseteq \mathbb{C}^n$.
  Assume that $G$ and $X$ are definable in $\mathbb{R}_{\exp}$.
  Then there is a complex algebraic set $A\subseteq \mathbb{C}^n$ such that $X $is an irreducible component of $A\cap G$.
\end{corollary}

\section{O-minimal GAGA Results}
O-minimal GAGA theorems are from \cite{zbMATH07662555},
which are used in the proof of the boundedness in \cite{arXiv:2507.00973,arXiv:2508.19215}
to adapt to the non-algebraic period domains from moduli spaces of abelian varieties.

\begin{tcolorbox}[title = {\bfseries\Large Main results}]
  \begin{theorem}[{Definable GAGA, \cite[Theorem 2.1]{arXiv:2508.19215},\cite[Theorem 1.4]{zbMATH07662555}}]
    Le $X$ be an algebraic space and $X^{\definable}$ the associated definable analytic space.
    The definabilization functor $\mathrm{Coh}(X) \to \mathrm{Coh}(X^{\definable})$ is fully faithful, exact and
    its essential image if closed under subobjects and quotients.
  \end{theorem}

  \begin{theorem}[{Definable images, \cite[Theorem 2.2]{arXiv:2508.19215},\cite[Theorem 1.3]{zbMATH07662555}}]
    \label{def image}
    Let $X$ be an algebraic space and
    $\phi: X^{\definable} \to \mathcal{Z}$ a proper morphism of definable analytic spaces.
    Then there is a factorization
    \[\begin{tikzcd}
      X^{\definable}\ar[rr,"\phi"]\ar[dr,"f^{\definable}"'] & & \mathcal{Z} \\
                                                            & Y^{\definable}\ar[ur,"\iota"'] &
    \end{tikzcd}\]
    where $f: X\to Y$ is a proper dominant morphism of algebraic spaces and
    $\iota: Y^{\definable} \to \mathcal{Z}$ is a closed embedding of definable analytic spaces.
    Moreover, $f$ is uniquely determined as a morphism with fixed source.
  \end{theorem}
\end{tcolorbox}

The following materials follow from \cite{zbMATH07662555}.

\subsection{Definable Analytic Spaces}
\subsubsection{Local case}
Identify $\mathbb{C} = \mathbb{R}^2$ using the real and imaginary parts,
and give $\mathbb{C}$ the definable structure coming from the identification $\mathbb{C}^n = \mathbb{R}^{2n}$.
For a definable open $U \subset \mathbb{C}^n$,
let $\mathcal{O}_{\mathbb{C}^n}(U)$ be the \emph{definable holomorphic} functions on $U$,
that is, the maps $U \to \mathbb{C}$ that are both definable and holomorphic.

\begin{definition}[Definition 2.19]
  Given an open definable subset $U \subset \mathbb{C}^n$ and
  a finitely generated ideal $I$ of $\mathcal{O}_{\mathbb{C}^n}(U)$,
  the vanishing locus $X = |V(I)|$ is naturally a definable topological space.
  We call the data of $U \subset \mathbb{C}^n$ and $I$ a \emph{basic definable complex analytic space}.
  We often refer to the basic definable complex analytic space via $X \subset U \subset \mathbb{C}^n$,
  and denote by $I_X := I\mathcal{O}_U$.
\end{definition}

\begin{theorem}[Definable Oka coherence, Theorem 2.21]
  The definable structure sheaf $\mathcal{O}_{\mathbb{C}^n}$ of $\mathbb{C}^n$ is a coherent $\mathcal{O}_{\mathbb{C}^n}$-module.
\end{theorem}

Given a basic definable complex analytic space $X \subset U \subset \mathbb{C}^n$,
we may naturally consider $X$ as an analytic space,
which is denoted $X^{\analytic}$.
For simplicity, denote $\mathbf{Coh}(X) := \mathbf{Coh}(\mathcal{O}_X)$ and
$\mathbf{Coh}(X^{\analytic}) := \mathbf{Coh}(\mathcal{O}_{X^{\analytic}})$.
There is a natural morphism $g: (X^{\analytic},\mathcal{O}_{X^{\analytic}}) \to (\underline{X},\mathcal{O}_X)$
of locally $\mathbb{C}$-ringed sites,
and a resulting analytification functor $(-)^{\analytic}: \mathbf{Coh}(X) \to \mathbf{Coh}(X^{\analytic})$
given by $F^{\analytic} := \mathcal{O}_{X^{\analytic}} \otimes_{g^{-1}\mathcal{O}_X} g^{-1}F$ together with
a natural identification $\mathcal{O}_X^{\analytic} \cong \mathcal{O}_{X^{\analytic}}$.

\begin{theorem}[Theorem 2.27]
  Let $X$ be a basic definable complex analytic space and
  $(-)^{\analytic} : \mathbf{Coh}(X) \to \mathbf{Coh}(X^{\analytic})$ the analytification functor.
  Then
  \begin{enumerate}[label = {(\arabic*)}]
    \item $(-)^{\analytic}$ is exact;
    \item $(-)^{\analytic}$ is faithful.
  \end{enumerate}
\end{theorem}

\subsubsection{Global case}
\begin{definition}[Definition 2.35]
  A locally $\mathbb{C}$-ringed definable space $(X,\mathcal{O}_X)$ is \emph{locally a basic definable complex analytic space}
  if on a definable cover it is isomorphic to the locally $\mathbb{C}$ definable space
  associated to a basic definable complex analytic space.
  We define the category of \emph{definable complex analytic spaces} (DefAnSp/$\mathbb{C}$) to be
  the full subcategory of the category of locally $\mathbb{C}$-ringed definable spaces consisting of $(X,\mathcal{O}_X)$
  which are locally a basic definable complex analytic space.
\end{definition}

\begin{theorem}[Theorem 2.38]
  Let $X$ be a definable complex analytic space.
  Then $\mathcal{O}_X$ is a coherent $\mathcal{O}_X$-module.
\end{theorem}

\begin{theorem}[Theorem 2.39]
  Let $X$ be a definable complex analytic space.
  Then the analytification functor
  $(-)^{\analytic}: \mathbf{Coh}(X) \to \mathbf{Coh}(X^{\analytic})$ is exact and faithful.
\end{theorem}

\begin{corollary}[Corollary 2.40]
  For $X$ a definable complex analytic space,
  a sequence $M' \to M \to M''$ of coherent $\mathcal{O}_X$-modules
  is exact if and only if it is exact on stalks (or even analytic stalks).
\end{corollary}

\subsubsection{Reduced case}
\begin{proposition}[Proposition 2.45]
  Let $X$ be a definable complex analytic space and
  $\mathcal{Y} \subset X$ a closed definable complex analytic subset.
  Then $\mathcal{Y}$ canonically has the structure of a reduced closed definable complex analytic subspace $Y \subset X$.
\end{proposition}

\subsubsection{Induction method}
\begin{proposition}[Definable Noetherian induction, Proposition 2.46]
  Let $X$ be a definable complex analytic space and $F$ a coherent sheaf on $X$.
  Any increasing chain of coherent subsheaves of $F$ must stabilize.
\end{proposition}

\subsubsection{Analytic factorization}
\begin{proposition}[Proposition 2.55] \label{analytic factorization}
  Let $X$, $Y$, $Z$ be definable complex analytic spaces and
  suppose we have (solid) diagrams
  \[
    \begin{tikzcd}
      X \ar[r,"h"] \ar[d,"g"'] & Y\ar[dl,"f",dotted] \\ Z
    \end{tikzcd}
    \hspace*{30pt}
    \begin{tikzcd}
      X^{\analytic} \ar[r,"h^{\analytic}"] \ar[d,"g^{\analytic}"'] & Y^{\analytic}\ar[dl,"\varphi"] \\ Z^{\analytic}
    \end{tikzcd}
  \]
  such that $h$ is proper, surjective on points,
  and $\mathcal{O}_Y \to h_*\mathcal{O}_X$ is injective.
  Then a unique $f$ exists such that $f^{\analytic} = \varphi$.
\end{proposition}

\subsection{Definable GAGA Theorem}
\hfill
\begin{tcolorbox}[title = {\Large Goal}]
  \begin{theorem}[Theorem 3.1]
    \label{def GAGA}
    Let $X$ be an algebraic space and
    \[(-)^{\definable} : \mathbf{Coh}(X) \to \mathbf{Coh}(X^{\definable})\]
    the definabilization functor.
    Then
    \begin{enumerate}[label = {(\arabic*)}]
      \item $(-)^{\definable}$ is fully faithful and exact.
      \item The essential image of $(-)^{\definable}$ is closed under taking subobjects and quotients.
    \end{enumerate}
  \end{theorem}
\end{tcolorbox}

\begin{theorem}[{Definable Chow theorem, Theorem 3.3, Peterzil--Strarchenko \cite[Corollary 4.5]{zbMATH05364146}}]
  Let $Y$ be a reduced algebraic space and
  $\mathcal{X} \subset Y^{\definable}$ a closed definable complex analytic subset.
  Then $\mathcal{X}$ is algebraic.
\end{theorem}

\begin{lemma}[Lemma 3.4]
  $(-)^{\definable}$ is faithful and exact.
\end{lemma}

\begin{lemma}[Lemma 3.5]
  \label{Lemma 3.5}
  Let $X$ be an algebraic space.
  Then Definable GAGA Theorem \ref{def GAGA} holds for $X$ if and only if
  for every algebraic coherent sheaf $F$ on $X$,
  any definable coherent subsheaf $\mathcal{E} \subset F^{\definable}$ is the definabilization of
  an algebraic coherent subsheaf $E \subset F$.
\end{lemma}

The two observations imply that Theorem \ref{def GAGA} holds for $X$
if and only if it holds on the reduction $X^{\mathrm{red}}$:
\begin{lemma}[Lemma 3.6]
  \label{Lemma 3.6}
  Let $X$ be an algebraic space with a nilpotent sheaf of ideals $I$ cutting out a subspace $X_0$.
  Then Theorem \ref{def GAGA} holds for $X_0$ if and only if it holds for $X$.
\end{lemma}

\begin{proof}[Proof of Theorem \ref{def GAGA}]
  Proceed by Noetherian induction on $X$,
  assuming that Theorem \ref{def GAGA} holds for every proper subspace of $X$.
  By \ref{Lemma 3.6}, $X$ can be assumed reduced.
  Let $F$ be an algebraic coherent sheaf on $X$ and $\mathcal{E} \subset F^{\definable}$ a definable coherent subsheaf.
  By Lemma \ref{Lemma 3.5} we must show that $\mathcal{E}$
  is the definabilization of an algebraic coherent subsheaf $E \subset F$.

  \begin{enumerate}[label = {\textit{Step \arabic*.}},
    itemsep = 2ex]
    \item
      \begin{lemma}[Lemma 3.7]
        Any exact sequence
        \[
          0 \to \mathcal{E} \to F^{\definable} \to \mathcal{G} \to 0
        \]
        in $\mathbf{Coh}(X^{\definable})$ for which $\mathcal{E}$ and $\mathcal{G}$ are locally free
        in the definabilization of an exact sequence
        \[
          0 \to E \to F \to G \to 0
        \]
        in $\mathbf{Coh}(X)$ where $E$ and $G$ are locally free.
      \end{lemma}

    \item
      \begin{lemma}[Lemma 3.8]
        For some dense open $U \subset X$, $\mathcal{E}_{|U}$ is algebraic.
      \end{lemma}

    \item
      With the notation above,
      let $E_U$ be the algebraic sheaf on $U$ for which $(E_U)^{\definable} \cong \mathcal{E}_{|U}$.
      Let $\widetilde{E}$ be the "closure" of $E_U$ in $F$, i.e.,
      the pullback
      \[\begin{tikzcd}
        F \ar[r] & j_*j^*F \\
        \widetilde{E} \ar[u]\ar[r] & j_*E_U \ar[u]
      \end{tikzcd}\]
      where $j: U \hookrightarrow X$ denotes the inclusion.
      The sheaf $\widetilde{E}$ is evidently quasi-coherent and so it is coherent since it is a subsheaf of $F$.
      Thus, $\widetilde{E}^{\definable}$ and $\mathcal{E}$ are both definable coherent subsheaves of $F^{\definable}$,
      and therefore so is their intersection $\mathcal{G}$.

      Let $I_Z$ be the ideal sheaf of $Z = X \backslash U$ with the reduced algebraic space structure,
      and $\mathcal{I} = I_Z^{\definable}$.
      \begin{lemma}[Lemma 3.9]
        Suppose we have definable coherent sheaves $\mathcal{G} \subset \mathcal{G}'$
        for which $\mathcal{G}_{|U} = \mathcal{G}'_{|U}$.
        Then for some positive integer $n$, $\mathcal{I}^n\mathcal{G}' \subset \mathcal{G}$.
      \end{lemma}
      Applying the lemma to $\mathcal{G} \subset \widetilde{E}^{\definable}$,
      we have $(I^n_Z\widetilde{E})^{\definable} \subset \mathcal{E}$ for some positive integer $n$.
      The quotient $\mathcal{E}'$ is then a subsheaf of $(F')^{\definable}$,
      where $F' = F/I^n_Z\widetilde{E}$ is supported on a subspace whose reduction is $Z$.
      By the induction hypothesis, $\mathcal{E}'$ is algebraic,
      and $\mathcal{E}$ is the preimage in $F$,
      hence algebraic, so the proof is complete.
  \end{enumerate}
\end{proof}

\begin{corollary}[Corollary 3.10]
  Let $Y$ be an algebraic space and $\mathcal{X} \subset Y^{\definable}$ a closed definable complex analytic subspace.
  Then $\mathcal{X}$ is (uniquely) the definabilization of an algebraic subspace.
\end{corollary}

\begin{corollary}[Corollary 3.11] \label{uniqueness of definabilization}
  Let $X$, $Y$ be algebraic spaces.
  Then any morphism $X^{\definable} \to Y^{\definable}$ of definable complex analytic space is (uniquely)
  the definabilization of an algebraic morphism.
\end{corollary}

\subsection{Definable Images}

\begin{definition}
  A morphism $f:X \to Y$ of algebraic spaces is \emph{dominant} if $\mathcal{O}_Y \to f_*\mathcal{O}_X$ is injective.
\end{definition}

\begin{tcolorbox}[title = {\Large Goal}]
  \begin{theorem} \label{proper factorization}
    Let $X$ be an algebraic space,
    $\mathcal{S}$ a definable complex analytic space,
    and $\varphi: X^{\definable} \to \mathcal{S}$ a proper definable complex analytic morphism.
    Then there exists a (unique) factorization
    \[\begin{tikzcd}
      X^{\definable}\ar[dr,"f^{\definable}"']\ar[rr,"\varphi"] & & \mathcal{S} \\
                                                               & Y^{\definable} \ar[ur,"\iota",hook] &
    \end{tikzcd}\]
    where $f: X \to Y$ is dominant algebraic and $\iota$ is a definable closed immersion.
    Moreover, $\iota^{\analytic}(Y^{\analytic})$ coincides with the image $\varphi^{\analytic}(X^{\analytic})$.
  \end{theorem}
\end{tcolorbox}

The proof involves two main steps:
the case that $X$ is reduced and the reduction to this case.

\begin{proposition}[Proposition 4.5] \label{thickening}
  Let $f: W \to Z$ be a proper dominant morphism of algebraic spaces.
  Suppose we have an algebraic square-zero thickening
  $W \to W'$, a definable closed immersion $Z^{\definable} \to \mathcal{Z}'$,
  and a morphism $\varphi': W^{\definable}\to \mathcal{Z}'$ which fits into a commutative diagram
  \[\begin{tikzcd}
    W^{\definable} \ar[r]\ar[d,"f^{\definable}"'] & W^{'\definable}\ar[d,"\varphi'"] \\
    Z^{\definable} \ar[r] & \mathcal{Z}'
  \end{tikzcd}\]
  Then the following are uniquely defined:
  an algebraic square-zero thickening
  $Z \to Z''$,
  a definable closed immersion $Z^{''\definable} \to \mathcal{Z}'$,
  and a (proper) dominant morphism $f': W' \to Z''$ of algebraic spaces,
  such that we have commutative diagrams
  \[
    \begin{tikzcd}
      W\ar[r]\ar[d,"f"'] & W'\ar[d,"f'"] \\
      Z \ar[r] & Z''
    \end{tikzcd}
    \hspace{40pt}
    \begin{tikzcd}
      W^{'\definable}\ar[dd,"f^{'\definable}"']\ar[rd,"\varphi'"] & \\
                                                                  & \mathcal{Z}' \\
      Z^{''\definable}\ar[ur] &
    \end{tikzcd}
  \]
\end{proposition}

\begin{proposition}[Proposition 4.6] \label{embedding into Hilb}
  Let $X$ be a smooth algebraic space,
  $\mathcal{U}$ a smooth definable complex analytic space,
  and $\varphi: X^{\definable} \to \mathcal{U}$ a smooth proper definable analytic morphism.
  Then $\varphi: X^{\definable} \to \mathcal{U}$ is the definabilization of an algebraic morphism $f: X \to U$ and
  the associated morphism $U \to \mathrm{Hilb}(X)$ is a closed embedding.
\end{proposition}

\begin{proof}[Proof of Theorem \ref{proper factorization}]
  The uniqueness property follows immediately from Proposition \ref{analytic factorization}, Corollary \ref{uniqueness of definabilization},
  and the corresponding uniqueness property of the analytic image, so we need only prove the existence of such a factorization.

  Proceed by induction on dimension, the base case being trivial.
  \begin{enumerate}
    \item 
    Propostion \ref{thickening} reduces to the case $X$ reduced.
    By Corollary \ref{uniqueness of definabilization} it suffices to algebrize $\mathcal{S}$.
    
    \item
    Reduce to the case that the analytification of $\varphi$ is a proper modification, that is, 
    $\varphi^\analytic: X^\analytic \to \mathcal{S}^\analytic$ is proper and induces an isomorphism 
    $(\phi^{\analytic})^{-1}(\mathcal{U})\to\mathcal{U}$ for a dense analytic Zariski open subset $\mathcal{U} \subset \mathcal{S}^{\analytic}$.

    Observe that $\varphi$ is smooth over a dense smooth definable Zariski open subset $\mathcal{U} \subset \mathcal{S}$.
    Apply Proposition \ref{embedding into Hilb}, we conclude that $\varphi_{\mathcal{U}} : X_{\mathcal{U}}^\definable \to \mathcal{U}$
    is the definabilization of $f_U: X \to U$ and that $U \to \mathrm{Hilb}(X_{\mathcal{U}})$ is a closed embedding.
    Evidently $f_U$ is the restriction of the universal family.

    Obviously $\mathrm{Hilb}(X_{\mathcal{U}})$ is an open subset of $\mathrm{Hilb}(X)$.
    Let $B$ be the closure of the image of $U$ in $\mathrm{Hilb}(X)$,
    $V_B \to B$ the restriction of the universal family,
    $\widetilde{B} \to B$ the normalization,
    and $V_{\widetilde{B}}\to B$ the base-change of the universal family. We then have solid diagrams
    \[\begin{tikzcd}
      &                           & V_{\widetilde{B}} \arrow[ld] \arrow[rd] &                          &  &                         & (V_{\widetilde{B}})^\definable \arrow[ld] \arrow[rd] \arrow[dd] &                                                     \\
      & V_B \arrow[rd] \arrow[ld] &                                         & \widetilde{B} \arrow[ld] &  & X^\definable \arrow[rd] &                                                                 & \widetilde{B}^\definable \arrow[ld, "\psi", dashed] \\
    X &                           & B                                       &                          &  &                         & \mathcal{S}                                                     &                                                    
    \end{tikzcd}\]
    The resulting morphism $\psi$ is a proper modification, as it is proper
    ($(V_{\widetilde{B}})^\definable \to \mathcal{S}$ is proper and $V_{\widetilde{B}}\to \widetilde{B}$ is surjective)
    and an isomorphism over $\mathcal{U}$.

    \item
    By the inductive hypothesis and definable Chow, the center of $X^\definable \to S$ can be algebraized.

    Let $Z^\definable \subset \mathcal{S}$ be the reduced center, and $W^\definable = \varphi^{-1}(Z^\definable)$
    equipped with its reduced induced structure.
    For every positive integer $k$, let $W_k$ be the $k$-th order thickening of $W$,
    and $\mathcal{Z}_k$ the $k$-th order thickening of $Z^\definable$ in $\mathcal{S}$.
    Induction gives the factorization of $\varphi_k: W_k^\definable \to \mathcal{S}$, namely
    \[
      W_k^\definable  \xlongrightarrow{f_k^\definable} \to \mathcal{S}.
    \]
    Let $\bar{W}$ be the completion of $X$ along $W$ and $\bar{Z} = \mathrm{colim} Z_k$,
    both of which are formal algebraic spaces; we then have a morphism $\bar{f}: \bar{W} \to \bar{Z}$. 
    
    \begin{lemma}[Lemma 4.7]
      $\bar{f}: \bar{W} \to \bar{Z}$ is a formal modification (see \cite[Definition (1.7)]{zbMATH03283964} for definition).
    \end{lemma}
    
    \begin{theorem}[Theorem 4.9, Artin, {\cite[Theorem (3.1)]{zbMATH03283964}}]
      Let $X$ be an algebraic space of finite type over a field, and $W\subset X$ be a closed subspace.
      Let $\bar{W}$ denote the formal completion of $X$ along $W$,
      and suppose that $\bar{f}: \bar{W} \to \bar{Z}$ is a formal modification.
      Then there is a modification $f:X \to S$ which is an isomorphism on the complement of $W$
      and such that the completion of $f$ along $W$ is isomorphic to $\bar{f}$.
    \end{theorem}
    
    We then conclude that $\varphi:X^\analytic \to \mathcal{S}^\analytic$ is algebraized by $f: X \to S$,
    and by Proposition \ref{analytic factorization} we have $S^\definable \cong \mathcal{S}$.
  \end{enumerate}
\end{proof}

\begin{lemma}[Lemma 4.11]
  Suppose $Z$ is an algebraic space,
  and $J$ is a coherent sheaf on $Z$.
  Let $R$ be a sheaf of rings on the {\'e}tale site $Z^{\text{\' et}}$ of $Z$ such that
  \[
    0 \to J \to R \to \mathcal{O}_Z \to 0
  \]
  is a first order thickening.
  Then $(Z^{\text{\'et}},R)$ is an algebraic space.
\end{lemma}

\emergencystretch = 1em
\printbibliography

\end{document}
